---
title: "Company Counts on GitHub"
author: "Brandon L. Kramer"
date: "11/26/2019"
output: html_document
---

```{r loading data}
rm(list = ls())

# load packages 
for (pkg in c("tidyverse", "igraph", "visNetwork", "data.table", "R.utils", "RPostgreSQL", "cowplot", "maditr", "stringr", "stringi")) {library(pkg, character.only = TRUE)}

# connect to postgresql to get our data
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# query the users_gh data from github data 
users_gh <- dbGetQuery(conn, "SELECT * 
                              FROM gh.ctrs_extra")

# disconnect from postgresql database 
dbDisconnect(conn)
```

```{r}

users_gh

length(users_gh$company) 
# 2,143,407 total entries 
# note: there are actually 2,435,698 total users

valid_company_codes <- users_gh %>% drop_na(company) 
length(valid_company_codes$company)
# 422517 users with some company_code information 
length(valid_company_codes$company) / length(users_gh$company)
# putting us at 19.7124% that are identifiable for now 

users_gh %>% 
  drop_na(company) %>% 
  mutate(organization = str_to_lower(company)) %>% 
  mutate(organization = str_trim(organization)) %>% 
  group_by(organization) %>% 
  count() %>% arrange(-n)

```

```{r company counts}
organization_counts <- users_gh %>% 
  drop_na(company) %>% 
  mutate(organization = str_to_lower(company)) %>% 
  mutate(organization = str_trim(organization)) %>% 
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)((?i)^self$|^personal$|^home$|^private$|^individual$|^myself$|^me$|^house$|^independent$|independent contractor|^consultant$|freelancer|freelance|freelancing|self employed|my home|me, myself|me myself|household|my house|jobless|looking for a job|looking for job|seeking employment|^seeking|seeking opportunities|seeking internship|seeking work|web developer|independent consultant|software developer|independent developer)\\b"), 
                              yes = "household", no = organization)) %>%
  group_by(organization) %>% count() %>% arrange(-n) 

organization_counts 

```

See also 

https://github.com/DSPG-Young-Scholars-Program/dspg20oss/blob/danBranch/ossPy/keyFiles/individualKeys.csv
https://github.com/DSPG-Young-Scholars-Program/dspg20oss/blob/danBranch/ossPy/keyFiles/nullKeys.csv


'(?i)^self$'
'(?i)^personal$'
'(?i)^home$'
'(?i)^private$'
'(?i)^individual$'
'(?i)^myself$'
'(?i)^me$'
'(?i)^house$'
'(?i)^independent$'
'(?i)independent contractor'
'(?i)^consultant$'
'(?i)freelancer'
'(?i)freelance'
'(?i)freelancing'
'(?i)self employed'
'(?i)my home'
'(?i)me, myself'
'(?i)me myself'
'(?i)household'
'(?i)my house'
'(?i)jobless'
'(?i)looking for a job'
'(?i)looking for job'
'(?i)seeking employment'
'(?i)^seeking$'
'(?i)seeking opportunities'
'(?i)seeking internship'
'(?i)seeking work'
'(?i)web developer'
'(?i)independent consultant'
'(?i)software developer'
'(?i)independent developer'




