---
title: "International Contributor Networks: Cumulative Stats"
author: "Brandon L. Kramer"
output: html_document
---

## Loading Data 

We used this code to pull data for the construction of Github network data (cumulatively.

```{r loading edgelist data, warning=FALSE, echo=FALSE}
rm(list = ls())
# install.packages(c("tidyverse", "igraph", "visNetwork", "bc3net", 
# "data.table", "R.utils", "RPostgreSQL", "cowplot", "maditr", "linkprediction", "poweRlaw"))

# load packages 
for (pkg in c("tidyverse", "igraph", "data.table", "R.utils", "RPostgreSQL",
              "cowplot", "maditr", "lubridate")) {library(pkg, character.only = TRUE)}

# connect to postgresql to get data (in rivanna)
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# query the bipartite edgelist data from github data  
ctr_edgelist <- dbGetQuery(conn, "SELECT ctr1, ctr2, year, repo_wts 
                                  FROM gh.sna_intl_ctr_edgelist
                                  WHERE year > 2007 AND year < 2017")

# disconnect from postgresql
dbDisconnect(conn)

# convert edgelist to network 
ctr_edgelist <- ctr_edgelist %>% 
  select(ctr1, ctr2, repo_wts) %>% 
  rename(from = ctr1, to = ctr2, weight = repo_wts) %>% 
  group_by(from, to) %>% 
  summarize(weight = sum(weight)) %>% 
  arrange(-weight)
  
login_network <- graph.data.frame(ctr_edgelist, directed = FALSE)
login_network <- simplify(login_network, remove.loops = TRUE)

```

```{r global network stats}
# loading the network (if the instance crashes while doing network_stats)
net_stats_start <- data.frame(event="net_stats_start", time=now("EST"))
network_stats <- data.frame(year="2008-16")                                          

# node and edge counts  
network_stats$node_count <- gorder(login_network)  
network_stats$edge_count <- gsize(login_network)
network_stats$commits <- sum(ctr_edgelist$weight)

# isolates, dyads and triads 
network_stats$isolates <- sum(degree(login_network)==0)
network_stats$dyads <- dyad_census(login_network)[1]
net_counts <- data.frame(event="net_counts", time=now("EST"))
time_log <- rbind(net_stats_start, net_counts); rm(net_stats_start, net_counts)

# density and transitivity
network_stats$density <- edge_density(login_network, loops=FALSE) 
network_stats$transitivity <- transitivity(login_network)
net_globals <- data.frame(event="net_globals", time=now("EST"))
time_log <- rbind(time_log, net_globals); rm(net_globals)

# community detection (using louvain method)
louvain <- cluster_louvain(login_network)
network_stats$louvain <- modularity(louvain)
network_stats$louvain_scaled <- modularity(louvain) / gorder(login_network)
network_stats$louvain_logged <- modularity(louvain) / log(gorder(login_network))
# community detection (using fast & greedy method)
fstgrdy <- fastgreedy.community(login_network)
network_stats$fstgrdy <- modularity(fstgrdy)
network_stats$fstgrdy_scaled <- modularity(fstgrdy) / gorder(login_network)
network_stats$fstgrdy_logged <- modularity(fstgrdy) / log(gorder(login_network))

# decomposition statistics 
decomposition_stats <- table(sapply(decompose.graph(login_network), vcount))

net_comm_det <- data.frame(event="net_comm_det", time=now("EST"))
time_log <- rbind(time_log, net_comm_det); rm(net_comm_det)

# now, we need to construct a nodelist 
nodelist <- data.frame(id = c(1:(igraph::vcount(login_network))), login = igraph::V(login_network)$name)

# degree, weighted degree, k core and modularity 
node_stats_start <- data.frame(event="node_stats_start", time=now("EST"))
time_log <- rbind(time_log, node_stats_start); rm(node_stats_start)
nodelist$degree <- degree(login_network)
nodelist$wtd_degree <- strength(login_network)
nodelist$k_core <- coreness(login_network)
#louvain <- cluster_louvain(login_network)
nodelist$louvain_comm <- louvain$membership
#fstgrdy <- fastgreedy.community(login_network)
#nodelist$fstgrdy_comm <- fstgrdy$membership
components <- components(login_network)
nodelist$component <- components$membership

node_stats_end <- data.frame(event="node_stats_end", time=now("EST"))
time_log <- rbind(time_log, node_stats_end); rm(node_stats_end, louvain, components)

setwd("~/oss-data/intl-dyn-ctr-nets-cum")
saveRDS(network_stats, "global_netstats_2008-16.rds")  
saveRDS(decomposition_stats, "decomposition_stats_2008-16.rds") 
saveRDS(nodelist, "nodelist_2008-16.rds")  
saveRDS(time_log, "timelog_2008-16.rds")
```

```{r binding cum nodelists}
# read nodelists
rm(list = ls())
setwd("~/oss-data/intl-dyn-ctr-nets-cum")
#setwd("~/oss_networks_cum/2008")
nodelist_2008 <- readRDS("nodelist_2008.rds") 
#setwd("~/oss_networks_cum/2008-09")
nodelist_200809 <- readRDS("nodelist_2008-09.rds") 
#setwd("~/oss_networks_cum/2008-10")
nodelist_200810 <- readRDS("nodelist_2008-10.rds")
#setwd("~/oss_networks_cum/2008-11")
nodelist_200811 <- readRDS("nodelist_2008-11.rds") 
#setwd("~/oss_networks_cum/2008-12")
nodelist_200812 <- readRDS("nodelist_2008-12.rds") 
#setwd("~/oss_networks_cum/2008-13")
nodelist_200813 <- readRDS("nodelist_2008-13.rds")
#setwd("~/oss_networks_cum/2008-14")
nodelist_200814 <- readRDS("nodelist_2008-14.rds")
#setwd("~/oss_networks_cum/2008-15")
nodelist_200815 <- readRDS("nodelist_2008-15.rds")
#setwd("~/oss_networks_cum/2008-16")
nodelist_200816 <- readRDS("nodelist_2008-16.rds")
#setwd("~/oss_networks_cum/2008-17")
nodelist_200817 <- readRDS("nodelist_2008-17.rds")
#setwd("~/oss_networks_cum/2008-18")
nodelist_200818 <- readRDS("nodelist_2008-18.rds")

full_nodelist <- nodelist_2008 %>% 
  select(-id) %>% 
  mutate(login = as.character(login)) %>% 
  rename(deg08 = degree,
         wtddeg08 = wtd_degree, 
         kcore08 = k_core,
         louvain08 = louvain_comm,
         #fstgrdy08 = fstgrdy_comm, 
         comp08 = component) %>%     
  right_join(nodelist_200809, by = "login") %>% 
  select(-id) %>% 
  rename(deg0809 = degree,
         wtddeg0809 = wtd_degree, 
         kcore0809 = k_core,
         louvain0809 = louvain_comm,
         #fstgrdy0809 = fstgrdy_comm,
         comp0809 = component) %>% 
  right_join(nodelist_200810, by = "login") %>% 
  select(-id) %>% 
  rename(deg0810 = degree,
         wtddeg0810 = wtd_degree, 
         kcore0810 = k_core,
         louvain0810 = louvain_comm,
         #fstgrdy0810 = fstgrdy_comm,
         comp0810 = component) %>% 
  right_join(nodelist_200811, by = "login") %>% 
  select(-id) %>% 
  rename(deg0811 = degree,
         wtddeg0811 = wtd_degree, 
         kcore0811 = k_core,
         louvain0811 = louvain_comm,
         #fstgrdy0811 = fstgrdy_comm,
         comp0811 = component) %>% 
  right_join(nodelist_200812, by = "login") %>% 
  select(-id) %>% 
  rename(deg0812 = degree,
         wtddeg0812 = wtd_degree, 
         kcore0812 = k_core,
         louvain0812 = louvain_comm,
         #fstgrdy0812 = fstgrdy_comm,
         comp0812 = component) %>% 
  right_join(nodelist_200813, by = "login") %>% 
  select(-id) %>% 
  rename(deg0813 = degree,
         wtddeg0813 = wtd_degree, 
         kcore0813 = k_core,
         louvain0813 = louvain_comm,
         #fstgrdy0813 = fstgrdy_comm,
         comp0813 = component) %>% 
  right_join(nodelist_200814, by = "login") %>% 
  select(-id) %>% 
  rename(deg0814 = degree,
         wtddeg0814 = wtd_degree, 
         kcore0814 = k_core,
         louvain0814 = louvain_comm,
         #fstgrdy0814 = fstgrdy_comm,
         comp0814 = component) %>% 
  right_join(nodelist_200815, by = "login") %>% 
  select(-id) %>% 
  rename(deg0815 = degree,
         wtddeg0815 = wtd_degree, 
         kcore0815 = k_core,
         louvain0815 = louvain_comm,
         #fstgrdy0815 = fstgrdy_comm,
         comp0815 = component) %>% 
  right_join(nodelist_200816, by = "login") %>% 
  select(-id) %>% 
  rename(deg0816 = degree,
         wtddeg0816 = wtd_degree, 
         kcore0816 = k_core,
         louvain0816 = louvain_comm,
         #fstgrdy0816 = fstgrdy_comm,
         comp0816 = component) %>% 
  right_join(nodelist_200817, by = "login") %>% 
  select(-id) %>% 
  rename(deg0817 = degree,
         wtddeg0817 = wtd_degree, 
         kcore0817 = k_core,
         louvain0817 = louvain_comm,
         #fstgrdy0817 = fstgrdy_comm,
         comp0817 = component) %>% 
  right_join(nodelist_200818, by = "login") %>% 
  select(-id) %>% 
  rename(deg0818 = degree,
         wtddeg0818 = wtd_degree, 
         kcore0818 = k_core,
         louvain0818 = louvain_comm,
         #fstgrdy0818 = fstgrdy_comm,
         comp0818 = component) 

setwd("~/oss-data/intl-dyn-ctr-nets-cum")
saveRDS(full_nodelist, "full_nodelist_cum.rds")
```

```{r concatenating global_netstats_cum}

setwd("~/oss-data/intl-dyn-ctr-nets-cum")
#setwd("~/2008")
global_netstats_2008 <- readRDS("global_netstats_2008.rds") 
#setwd("~/2008-09")
global_netstats_200809 <- readRDS("global_netstats_2008-09.rds") 
#setwd("~/2008-10")
global_netstats_200810 <- readRDS("global_netstats_2008-10.rds") 
#setwd("~/2008-11")
global_netstats_200811 <- readRDS("global_netstats_2008-11.rds") 
#setwd("~/2008-12")
global_netstats_200812 <- readRDS("global_netstats_2008-12.rds")
#setwd("~/2008-13")
global_netstats_200813 <- readRDS("global_netstats_2008-13.rds")
#setwd("~/2008-14")
global_netstats_200814 <- readRDS("global_netstats_2008-14.rds")
#setwd("~/2008-15")
global_netstats_200815 <- readRDS("global_netstats_2008-15.rds")
#setwd("~/2008-16")
global_netstats_200816 <- readRDS("global_netstats_2008-16.rds")
#setwd("~/2008-17")
global_netstats_200817 <- readRDS("global_netstats_2008-17.rds")
#setwd("~/2008-18")
global_netstats_200818 <- readRDS("global_netstats_2008-18.rds")

global_netstats_cum <- rbind(global_netstats_2008, global_netstats_200809,
                             global_netstats_200810, global_netstats_200811, 
                             global_netstats_200812, global_netstats_200813, 
                             global_netstats_200814, global_netstats_200815, 
                             global_netstats_200816, global_netstats_200817, global_netstats_200818) 

global_netstats_cum <- as_tibble(c("2008", "2009", "2010", "2011", "2012", 
                                   "2013", "2014", "2015", "2016", "2017", "2018")) %>% 
  bind_cols(global_netstats_cum) %>% # select(-year) %>% 
  rename(time = value)

setwd("~/intl-dyn-ctr-nets-cum"); saveRDS(global_netstats_cum, "global_netstats_cum.rds") 

# adding in weighted degree counts 

setwd("~/intl-dyn-ctr-nets-cum")
full_nodelist_cum <- readRDS("full_nodelist_cum.rds")
global_netstats_cum <- readRDS("global_netstats_cum.rds")

edges <- as_tibble(c(sum(full_nodelist_cum$deg08/ 2, na.rm = TRUE), sum(full_nodelist_cum$deg0809/ 2, na.rm = TRUE),
            sum(full_nodelist_cum$deg0810/ 2, na.rm = TRUE), sum(full_nodelist_cum$deg0811/ 2, na.rm = TRUE),
            sum(full_nodelist_cum$deg0812/ 2, na.rm = TRUE), sum(full_nodelist_cum$deg0813/ 2, na.rm = TRUE),
            sum(full_nodelist_cum$deg0814/ 2, na.rm = TRUE), sum(full_nodelist_cum$deg0815/ 2, na.rm = TRUE),
            sum(full_nodelist_cum$deg0816/ 2, na.rm = TRUE), sum(full_nodelist_cum$deg0817/ 2, na.rm = TRUE), 
            sum(full_nodelist_cum$deg0818/ 2, na.rm = TRUE))) 

weighted <- as_tibble(c(sum(full_nodelist_cum$wtddeg08, na.rm = TRUE), sum(full_nodelist_cum$wtddeg0809, na.rm = TRUE),
            sum(full_nodelist_cum$wtddeg0810, na.rm = TRUE), sum(full_nodelist_cum$wtddeg0811, na.rm = TRUE),
            sum(full_nodelist_cum$wtddeg0812, na.rm = TRUE), sum(full_nodelist_cum$wtddeg0813, na.rm = TRUE),
            sum(full_nodelist_cum$wtddeg0814, na.rm = TRUE), sum(full_nodelist_cum$wtddeg0815, na.rm = TRUE),
            sum(full_nodelist_cum$wtddeg0816, na.rm = TRUE), sum(full_nodelist_cum$wtddeg0817, na.rm = TRUE), 
            sum(full_nodelist_cum$wtddeg0818, na.rm = TRUE))) 

colnames(weighted) <- "wtd_edge_count"
global_netstats_cum <- cbind(global_netstats_cum, weighted) 
global_netstats_cum <- global_netstats_cum %>% 
  select(time, year, node_count, edge_count, wtd_edge_count, everything()) %>% 
  transform(dyads = as.numeric(dyads))

global_netstats_cum

```

```{r k_core}

setwd("~/intl-dyn-ctr-nets-cum")
full_nodelist <- readRDS("full_nodelist_cum.rds")
global_netstats_cum <- readRDS("global_netstats_cum.rds")

# get k_core data from nodelist
k08<-full_nodelist %>% drop_na(kcore08) %>% 
  count(kcore08) %>% rename(core = kcore08, k08 = n)
k09<-full_nodelist %>% drop_na(kcore0809) %>% 
  count(kcore0809) %>% rename(core = kcore0809, k09 = n)
k10<-full_nodelist %>% drop_na(kcore0810) %>% 
  count(kcore0810) %>% rename(core = kcore0810, k10 = n)
k11<-full_nodelist %>% drop_na(kcore0811) %>% 
  count(kcore0811) %>% rename(core = kcore0811, k11 = n)
k12<-full_nodelist %>% drop_na(kcore0812) %>% 
  count(kcore0812) %>% rename(core = kcore0812, k12 = n)
k13<-full_nodelist %>% drop_na(kcore0813) %>% 
  count(kcore0813) %>% rename(core = kcore0813, k13 = n)
k14<-full_nodelist %>% drop_na(kcore0814) %>% 
  count(kcore0814) %>% rename(core = kcore0814, k14 = n)
k15<-full_nodelist %>% drop_na(kcore0815) %>% 
  count(kcore0815) %>% rename(core = kcore0815, k15 = n)
k16<-full_nodelist %>% drop_na(kcore0816) %>% 
  count(kcore0816) %>% rename(core = kcore0816, k16 = n)
k17<-full_nodelist %>% drop_na(kcore0817) %>% 
  count(kcore0817) %>% rename(core = kcore0817, k17 = n)
k18<-full_nodelist %>% drop_na(kcore0818) %>% 
  count(kcore0818) %>% rename(core = kcore0818, k18 = n)

# join it all together 
kcore_data <- right_join(k08,k09, by = "core")  
kcore_data <- right_join(kcore_data,k10, by = "core")  
kcore_data <- right_join(kcore_data,k11, by = "core")
kcore_data <- right_join(kcore_data,k12, by = "core")
kcore_data <- right_join(kcore_data,k13, by = "core")
kcore_data <- right_join(kcore_data,k14, by = "core")
kcore_data <- right_join(kcore_data,k15, by = "core")
kcore_data <- right_join(kcore_data,k16, by = "core")
kcore_data <- right_join(kcore_data,k17, by = "core")
kcore_data <- right_join(kcore_data,k18, by = "core")

# adding max_kcore to df 
kmax_df = data.frame()
kmax_df <- data.frame(time = c("2008","2009","2010","2011","2012",
                               "2013","2014","2015","2016","2017","2018"))
kmax_df[,2] <- data.frame(kmax = c(max(k08$core),max(k09$core),max(k10$core),max(k11$core),
                               max(k12$core),max(k13$core),max(k14$core),max(k15$core),
                               max(k16$core),max(k17$core),max(k18$core)))

global_netstats_cum <- right_join(global_netstats_cum,kmax_df, by = "time")

setwd("~/intl-dyn-ctr-nets-cum")
write_rds(kcore_data, "kcore_data_cum.rds")
write_rds(global_netstats_cum, "global_netstats_cum.rds")

```

```{r decomp_stats}

setwd("~/intl-dyn-ctr-nets-cum")
dc08 <- as.data.frame(readRDS("decomposition_stats_2008.rds")) %>% rename(decomp = Var1, dc08 = Freq)
dc09 <- as.data.frame(readRDS("decomposition_stats_2008-09.rds")) %>% rename(decomp = Var1, dc09 = Freq)
dc10 <- as.data.frame(readRDS("decomposition_stats_2008-10.rds")) %>% rename(decomp = Var1, dc10 = Freq)
dc11 <- as.data.frame(readRDS("decomposition_stats_2008-11.rds")) %>% rename(decomp = Var1, dc11 = Freq)
dc12 <- as.data.frame(readRDS("decomposition_stats_2008-12.rds")) %>% rename(decomp = Var1, dc12 = Freq)
dc13 <- as.data.frame(readRDS("decomposition_stats_2008-13.rds")) %>% rename(decomp = Var1, dc13 = Freq)
dc14 <- as.data.frame(readRDS("decomposition_stats_2008-14.rds")) %>% rename(decomp = Var1, dc14 = Freq)
dc15 <- as.data.frame(readRDS("decomposition_stats_2008-15.rds")) %>% rename(decomp = Var1, dc15 = Freq)
dc16 <- as.data.frame(readRDS("decomposition_stats_2008-16.rds")) %>% rename(decomp = Var1, dc16 = Freq)
dc17 <- as.data.frame(readRDS("decomposition_stats_2008-17.rds")) %>% rename(decomp = Var1, dc17 = Freq)
dc18 <- as.data.frame(readRDS("decomposition_stats_2008-18.rds")) %>% rename(decomp = Var1, dc18 = Freq)

decomp_data_cum <- right_join(dc08,dc09, by = "decomp")  
decomp_data_cum <- right_join(decomp_data_cum,dc10, by = "decomp")  
decomp_data_cum <- right_join(decomp_data_cum,dc11, by = "decomp")
decomp_data_cum <- right_join(decomp_data_cum,dc12, by = "decomp")
decomp_data_cum <- right_join(decomp_data_cum,dc13, by = "decomp")
decomp_data_cum <- right_join(decomp_data_cum,dc14, by = "decomp")
decomp_data_cum <- right_join(decomp_data_cum,dc15, by = "decomp")
decomp_data_cum <- right_join(decomp_data_cum,dc16, by = "decomp")
decomp_data_cum <- right_join(decomp_data_cum,dc17, by = "decomp")
decomp_data_cum <- right_join(decomp_data_cum,dc18, by = "decomp")

setwd("~/intl-dyn-ctr-nets-cum")
write_rds(decomp_data_cum, "decomp_data_cum.rds")

```


##################################################### 
#####################################################
##################################################### NOT DONE YET 
#####################################################
#####################################################

## Calculating Power Laws Based on Degree Distribution of Networks (Not Done)

```{r fitting power laws}
power_law_start <- data.frame(event="power_law_start", time=now("EST"))
time_log <- rbind(time_log, power_law_start); rm(power_law_start)

data <- nodelist$degree
data.dist <- data.frame(k=0:max(data),p_k=degree_distribution(login_network))
data.dist <- data.dist[data.dist$p_k>0,]
ggplot(data.dist) + geom_point(aes(x=k, y=p_k)) + theme_bw()

m_pl <- displ$new(data)
est_pl <- estimate_xmin(m_pl)
est_pl$xmin # initial estimation of kmin 
est_pl$pars # initial estimation of γ
est_pl$gof # calculate D with Kolgomorov-Smirnov test

# finish remainder of process using https://rpubs.com/lgadar/power-law

power_law_end <- data.frame(event="power_law_end", time=now("EST"))
time_log <- rbind(time_log, power_law_end); rm(power_law_end)
```

## Normalizing Degree Distribributions with Cosine Similarity Scores (Not Done Yet)

```{r normalizing networks}
cos_norm <- proxfun(login_network, method="cos", value="edgelist") %>% 
  filter(from < to) %>% 
  rename(cos_norm = value)
```

## Testing for Assortativity and Homophily (Not Done Yet)

```{r testing patterns in assortativity and homophily}
# connect to postgresql to get data (in rivanna)
conn <- dbConnect(drv = PostgreSQL(), dbname = "sdad_data", 
                  host = "sdad.policy-analytics.net", port = 5436, 
                  user = Sys.getenv("db_userid"), password = Sys.getenv("db_pwd"))

# query the bipartite edgelist data from github data  
node_attributes <- dbGetQuery(conn, "SELECT name, country_code_vis
                                 FROM github.intl_st_bp_nodes")
# disconnect from postgresql
dbDisconnect(conn); rm(conn)

# adding country codes to the nodelist 
nodelist <- dplyr::full_join(nodelist, node_attributes, by = c("nName" = "login")) %>% 
  dplyr::mutate(new_col = ifelse(test = is.na(x = country_code), yes = paste("repo"), no = country_code)) %>% 
  dplyr::select(-country_code) %>% 
  dplyr::rename(name = nName, country_code = new_col)

# testing homophily based on country_code
assortativity_nominal(net, V(net)$media.type, directed=F)

# using linkprediction to test for structural homophily 



```

## References 

Blondel, V. D., Guillaume, J. L., Lambiotte, R., & Lefebvre, E. (2008). Fast unfolding of communities in large networks. Journal of statistical mechanics: theory and experiment, 2008(10), P10008.

http://pablobarbera.com/big-data-upf/html/02b-networks-descriptive-analysis.html
https://igraph.org/r/doc/cluster_louvain.html
https://kateto.net/networks-r-igraph 
https://sites.fas.harvard.edu/~airoldi/pub/books/BookDraft-CsardiNepuszAiroldi2016.pdf
https://rpubs.com/lgadar/power-law 
http://recon.icm.edu.pl/wp-content/uploads/2019/05/linkprediction.pdf


































