---
title: "GitHub Totals, By Country"
output: html_document
---

This code pulls from original commits data and groups by slug and country so that repos per country can be calculated.

```{sql }
CREATE MATERIALIZED VIEW AS gh.commits_by_repo_cc AS (
SELECT slug, country_code, COUNT(*) AS commits, SUM(additions) AS additions, SUM(deletions) AS deletions
FROM (SELECT slug, 
	  commits.login, 
	  EXTRACT(YEAR FROM committed_date)::int AS YEAR, 
	  users_gh_cc.country_code AS country_code, 
	  additions, deletions
	  FROM gh.commits 
	  FULL JOIN github.users_gh_cc 
	  ON commits.login = users_gh_cc.login) A
GROUP BY slug, A.country_code
); 
```

After that, we pull that data into R for repos_by_ctry and the nodelist with valid country_code only.

```{r setup, include=FALSE}
#rm(list = ls())
# load packages 
for (pkg in c("tidyverse", "data.table", "countrycode",
              "R.utils", "RPostgreSQL")) {library(pkg, character.only = TRUE)}

# connect to postgresql to get data (in rivanna)
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

repos_by_ctry <- dbGetQuery(conn, "SELECT slug, country_code, commits, additions, deletions
                                   FROM gh.commits_by_repo_cc
                                   WHERE country_code IS NOT NULL")

# disconnect from postgresql
dbDisconnect(conn)

# connect to postgresql to get data (in rivanna)
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

ctrs_by_ctry <- dbGetQuery(conn, "SELECT login, country_code, country_code_di, country_code_vis
                                  FROM gh.login_ctry_codes
                                  WHERE country_code IS NOT NULL")

# disconnect from postgresql
dbDisconnect(conn)
```

Then we calculate users by country... 

```{r}
# get the total logins by country 
stats_by_country <- ctrs_by_ctry %>% 
  group_by(country_code_vis) %>% 
  count() %>%
  rename(users = n, 
         country_code = country_code_vis) %>% 
  arrange(-users)

stats_by_country
```

Next, we pull in repos per country and recode the multiple column... 

```{r}
# recodes all of the countries with multiple names into one "multiple" category 
repos_by_ctry <- repos_by_ctry %>% 
  dplyr::mutate(old_cc = country_code) %>% 
  dplyr::mutate(country_code = ifelse(
    test = str_detect(string = country_code, 
                      pattern = "_"), paste("multiple"), no = country_code)) 

repos_by_ctry$country_code <- trimws(repos_by_ctry$country_code)

repos_by_ctry %>% 
  #grepl("us", "us")
  filter(country_code == "us")

# distinct countries 
n_distinct(repos_by_ctry$country_code)

# distinct slugs 
n_distinct(repos_by_ctry$slug)

```

Then we calculate repos, commits, additions, deletions, additions + deletions and additions - deletions by country... 

```{r}
# total repos by country 
stats_by_country <- repos_by_ctry %>% 
  group_by(country_code) %>% 
  count() %>% 
  rename(repos = n) %>% 
  right_join(stats_by_country, by = "country_code") %>%    
  select(country_code, users, repos) %>% 
  arrange(-repos)

# total commits by country 
stats_by_country <- repos_by_ctry %>% 
  drop_na(commits) %>% 
  group_by(country_code) %>% 
  summarise(commits = sum(commits)) %>% 
  right_join(stats_by_country, by = "country_code") %>%    
  select(country_code, users, repos, commits) %>% 
  arrange(-commits)
  
# total additions by country 
stats_by_country <- repos_by_ctry %>% 
  drop_na(additions) %>% 
  group_by(country_code) %>% 
  summarise(additions = sum(additions)) %>% 
  right_join(stats_by_country, by = "country_code") %>% 
  arrange(-additions) %>% 
  select(country_code, users, repos, commits, additions)

# total deletions by country 
stats_by_country <- repos_by_ctry %>% 
  drop_na(deletions) %>%
  group_by(country_code) %>% 
  summarise(deletions = sum(deletions)) %>% 
  right_join(stats_by_country, by = "country_code") %>% 
  arrange(-deletions) %>% 
  select(country_code, users, repos, commits, additions, deletions)

# total additions + deletions by country 
stats_by_country <- stats_by_country %>% 
  group_by(country_code) %>% 
  mutate(adds_plus_dels = sum(additions + deletions))

# total additions - deletions by country 
stats_by_country <- stats_by_country %>% 
  group_by(country_code) %>% 
  mutate(adds_minus_dels = sum(additions - deletions))

# all stats by repo 
stats_by_country <- stats_by_country %>% 
  mutate(cmts_per_repo = commits   / repos) %>% 
  mutate(adds_per_repo = additions / repos) %>% 
  mutate(dels_per_repo = deletions / repos) %>% 
  arrange(-users)

# changing country codes to country name 
stats_by_country$country <- countrycode(stats_by_country$country_code, 
                                        origin = 'iso2c', destination = 'country.name')

# changing Kosovo to have a valid country name 
stats_by_country <- stats_by_country %>% 
  mutate(country = ifelse(test = str_detect(string = country_code, 
                                            pattern = "xk"), yes = "Kosovo", no = country)) %>% 
  mutate(country = ifelse(test = str_detect(string = country_code, 
                                            pattern = "multiple"), yes = "Multiple Countries", no = country)) %>% 
  mutate(country = ifelse(test = str_detect(string = country_code, 
                                            pattern = "asia"), yes = "Asia", no = country)) %>% 
  mutate(country = ifelse(test = str_detect(string = country_code, 
                                            pattern = "europe"), yes = "Europe", no = country)) %>% 
  mutate(country = ifelse(test = str_detect(string = country_code, 
                                            pattern = "americas"), yes = "The Americas", no = country)) %>% 
  mutate(country = ifelse(test = str_detect(string = country_code, 
                                            pattern = "africa"), yes = "Africa", no = country)) %>%
  select(country, country_code, everything())

setwd("~/oss-data/intl-country-nets")
write_csv(stats_by_country, "oss-repos-per-country.csv")
```

And write our summary table to the database... 

```{r writing stats_by_country to the database}
# reconnecting to the database 
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# writing the new users_gh_cc table to postgis_2
dbWriteTable(conn, name = c(schema = "gh" , name = "intl_stats"), 
             value = stats_by_country, row.names = FALSE)

# disconnect from postgresql database  
dbDisconnect(conn)
```












