---
title: "Company Counts on GitHub"
author: "Brandon L. Kramer"
date: "11/26/2019"
output: html_document
---

```{r loading data}
rm(list = ls())

# load packages 
for (pkg in c("tidyverse", "igraph", "visNetwork", "data.table", "R.utils", "RPostgreSQL", "cowplot", "maditr", "stringr", "stringi")) {library(pkg, character.only = TRUE)}

# connect to postgresql to get our data
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# query the users_gh data from github data 
users_gh <- dbGetQuery(conn, "SELECT login, company, created_at 
                              FROM github.users_gh")

# disconnect from postgresql database 
dbDisconnect(conn)
```
```{r}

users_gh

length(users_gh$company) 
# 2,143,407 total entries 
# note: there are actually 2,435,698 total users

valid_company_codes <- users_gh %>% drop_na(company) 
length(valid_company_codes$company)
# 422517 users with some company_code information 
length(valid_company_codes$company) / length(users_gh$company)
# putting us at 19.7124% that are identifiable for now 

```

```{r company counts}
hyphen <- "[-]"
parentheses <- "[()]"
ellipses <- "[...]"

organization_counts <- users_gh %>% 
  # remove all na's 
  drop_na(company) %>% 
  # convert to lower case 
  mutate(organization = str_to_lower(company)) %>% 
  # remove @ from start of names 
  mutate(organization = str_replace_all(organization, "@", " ")) %>% 
  mutate(organization = str_replace_all(organization, "\\b(inc.|inc)\\b", "")) %>%
  mutate(organization = str_trim(organization)) %>% 
  # variations on major corporations 
  # these regex patterns were developed by (1) looking through the list and consolidating duplicate names and (2) using grepl to find lines with matching strings 
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^microsoft|microsoftedge|microsoftdocs|microsoftresearch|microsoftazure|microsoftdocs magfest|microsoftdotcom|microsoftgraph|microsoftleap|microsoftresearchasia|microsoftstudentpartners|microsoftwareltd|nextmicrosoft)\\b"), 
                              yes = "microsoft", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
  pattern = "\\b(?i)(^google|googlecloudplatform|googlechrome|googlecreativelab|googleapis|googlebd|googlecreativelab|googledevelopers|googlefonts|googlei18n|googlepixel2rom|livegoogle|mlgoogle)\\b"), 
                              yes = "google", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(ibm|ibm research|ibmresearch|ibmstreams|ibmruntimes|ibmets)\\b"), 
                              yes = "ibm", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(red hat|red hat, inc.|redhat|red hat, inc|red hat inc.|red hat inc|redhatofficial)\\b"), 
                              yes = "red hat", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(amazon|amazon web services|aws|amazon.com|amzn|amazonwebservice|awslabs|awsdocs|awssat|awscloud|awsteams|mobileaws)\\b"), 
                              yes = "amazon/aws", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^facebook|^facebook,|facebookresearch|facebook$|facebbok)\\b"), 
                              yes = "facebook", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^instagram|instagram$)\\b"), 
                              yes = "instagram", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(thoughtworks|thoughtworksinc|thoughtworksstudios)\\b"), 
                              yes = "thoughtworks", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(alibaba|alibaba group|alibabab|alibabab.|alibabacloud|alibabadp|alibabagroup|alibabapai)\\b"), 
                              yes = "alibaba", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(sap|sap se)\\b"), 
                              yes = "sap", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(tencent|^tencent|tencentafrica|tencentopen|tencentxtest)\\b"), 
                              yes = "tencent", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
  pattern = "\\b(?i)(mozilla|mozilla corporation|mozillafoundation|mozillabrasil raincorn|mozillahispano|mozillaitalia|mozillaonline|mozillareality|mozillascience|mozillaslovenija|mozillatn)\\b"), 
                              yes = "mozilla", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
pattern = "\\b(?i)(cisco|^cisco systems|ciscosystems|ciscodevnet|ciscoemerge|ciscocloud|ciscospark|ciscosystems datacenter|ciscosytems)\\b"), 
                              yes = "cisco systems", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(apple|apple inc.|apple inc)\\b"), 
                              yes = "apple", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(adobe|adobe systems)\\b"), 
                              yes = "adobe", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^oracle |^oracle,)\\b"), 
                              yes = "oracle", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^esri |^esri,|esri-es|esri-devcenter-beijing|esricanada|esriuk)\\b"), 
                              yes = "esri", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(salesforce|salesforce.com|salesforcefoundation|salesforceiq|salesforcesaturdaytokyo)\\b"), 
                              yes = "salesforce", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^shopify)\\b"), 
                              yes = "shopify", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(samsung|samsung electronics|samsungartik|samsungaccelerator|samsung360vr|samsunginternet|samsungsds)\\b"), 
                              yes = "samsung", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(yahoo|yahoo!|yahoojapan)\\b"), 
                              yes = "yahoo", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(uber|uber technologies|uberresearch|uber technologies,)\\b"), 
                              yes = "uber", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^twitter|^twitter,|^twitter:|twitter$)\\b"), 
                              yes = "twitter", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
  pattern = "\\b(?i)(^pivotal|^pivotal-cf|pivotal$|pivotal-cf$|pivotal labs$|pivotal-energy-solutions|pivotal-japan|^pivotalservices|pivotalsoftware|pivotaltracker)\\b"), 
                              yes = "pivotal", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(intel|intel coroporation)\\b"), 
                              yes = "intel", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^linkedin|linkedin$|contato-linkedin|^linkedin,)\\b"), 
                              yes = "linkedin", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(wix|wix.com)\\b"), 
                              yes = "wix", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
  pattern = "\\b(?i)(^hewlett packard|hewlett packard$|^hewlett-packard|^hewlettpackard|hewlettpackard$|hewlett-packard$)\\b"), 
                              yes = "hewlett packard", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^yandex|^yandex,|yandex$|yandex-money|yandexclassifieds|yandex-money-tech)\\b"), 
                              yes = "yandex", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^vmware|^vmware,|vmware$|vmware/lightwave)\\b"), 
                              yes = "vmware", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^accenture|accenture$|^accenture,)\\b"), 
                              yes = "accenture", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(cyberagent|cyberagent, .)\\b"), 
                              yes = "cyberagent", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(baidu .|baidu|baidu, .)\\b"), 
                              yes = "baidu", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^bloomberg|bloomberg l.p.)\\b"), 
                              yes = "bloomberg", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(slack|slackhq)\\b"), 
                              yes = "slack", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)($airbnb|airbnb$|$air bnb|air bnb$)\\b"), 
                              yes = "airbnb", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)($netlfix|$netlfix,|netflix$)\\b"), 
                              yes = "netflix", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^andela|^andela,|andela$)\\b"), 
                              yes = "andela", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^epam|^epam,|epam$)\\b"), 
                              yes = "epam systems", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^spotify|spotify$)\\b"), 
                              yes = "spotify", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^zendesk|zendesk$)\\b"), 
                              yes = "zendesk", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^netease|^netease,|netease$)\\b"), 
                              yes = "netease", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^suse| suse$)\\b"), 
                              yes = "suse", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^naver|naver$|naverlabs|naverbusinessplatform|uwnlp naver)\\b"), 
                              yes = "naver", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^preferred networks|^preferred networks,|preferred networks$)\\b"), 
                              yes = "preferred networks", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^red ventures|^redventures|red ventures$)\\b"), 
                              yes = "red ventures", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^credit karma|creditkarma)\\b"), 
                              yes = "credit karma", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^yelp|yelp!|yelp$|^yelp,)\\b"), 
                              yes = "yelp", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^atlassian|atlassian$)\\b"), 
                              yes = "atlassian", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^nvidia|nvidia$)\\b"), 
                              yes = "nvidia", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^zalando|zalando$)\\b"), 
                              yes = "zalando", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^automattic|automattic$)\\b"), 
                              yes = "automattic", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^huawei|^huawei,|huawei$)\\b"), 
                              yes = "huawei", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^rackspace|rackspace$)\\b"), 
                              yes = "rackspace", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^capgemini|capgemini$)\\b"), 
                              yes = "capgemini", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^jetbrains|jetbrains$)\\b"), 
                              yes = "jetbrains", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^cern|^cern,|cern$)\\b"), 
                              yes = "cern", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^bbc|^bbc,|bbc$|british broadcasting corporation)\\b"), 
                              yes = "bbc", no = organization)) %>%
  # universities and research institutes 
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(duke university|duke|duke university libraries|dukeuniversity)\\b"), 
                              yes = "duke university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
  pattern = "\\b(?i)(stanford university|stanford|stanfordmlgroup|stanfordvl|stanfordgeospatialcenter|stanfordhci|stanfordjournalism|stanfordmsl|stanfordnlp)\\b"), 
                              yes = "stanford university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(massachusetts institute of technology|mit|mitmedialab|mit media lab)\\b"), 
                              yes = "massachusetts institute of technology", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(harvard medical school|harvard|harvard university|harvardagileroboticslab|harvardnlp|harvardx)\\b"), 
                              yes = "harvard university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^princeton university|princeton university$|princetonuniversity|princeton)\\b"), 
                              yes = "princeton university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
  pattern = "\\b(?i)(^columbia university|columbia university$|barnard college|columbia-university)\\b"), 
                              yes = "columbia university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
  pattern = "\\b(?i)(^northeastern university|northeastern university$|northeastern)\\b"), 
                              yes = "northeastern university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
  pattern = "\\b(?i)(^northwestern university|northwestern university$|northwestern)\\b"), 
                              yes = "northwestern university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
  pattern = "\\b(?i)(^cornell university|cornell university$|northwestern|^cornell tech|cornell tech$|cornelltech|^weill cornell|weill cornell$|weill cornell medicine$|cornell|cornell lab of ornithology|cornell-dti|cornell-rpal|cornell asl|weillcornell nygenome|cornell cs|cornell unveristy|cs, cornell)\\b"), 
                              yes = "cornell university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
  pattern = "\\b(?i)(carnegie mellon|carnegie mellon university|carnegie mellon university software engineering institute|carnegie mellon university, silicon valley)\\b"), 
                              yes = "carnegie mellon university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(john hopkins|john hopkins university|johns hopkins university applied physics laboratory)\\b"), 
                              yes = "john hopkins university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(penn|upenn|pennlabs|university of pennsylvania|the university of pennsylvania|penn medicine)\\b"), 
                              yes = "university of pennsylvania", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
  pattern = "\\b(?i)(university of washington|university of washington(?! state)|univerisity of washington|univeristy of washington|universityofwashington|univesity of washington)\\b"),
                              yes = "university of washington system", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(university of california, san diego|university of california san diego|ucsd|university of california berkeley|uc berkeley|ucla|university of california, berkeley|university of california davis|university of california, davis|university of california irvine|university of california, irvine|california digital library, ucop|california digital library|university of california, san francisco|uc san francisco|university of california san francisco|uc san diego|uc davis)\\b"), 
                              yes = "university of california system", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
  pattern = "\\b(?i)(^california state|california state$|california state university$|^california polytechnic|california polytechnic$)\\b"), 
                              yes = "california state university system", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^georgia institute of technology|^georgia tech|georgia institute of technology$|georgia tech$)\\b"), 
                              yes = "georgia institute of technology", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(university of british columbia|ubc)\\b"), 
                              yes = "university of british columbia", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(indiana university|indiana university bloomington|indiana university, bloomington)\\b"), 
                              yes = "indiana university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(university of texas at austin|university of texas|the university of texas at austin)\\b"), 
                              yes = "university of texas", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^texas a&m|^texas a & m|texas a&m university)\\b"), 
                              yes = "texas a&m university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(university of college london|ucl|university college london)\\b"), 
                              yes = "university of college london", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(new york university|nyu|nyulibraries|nyueserv|itpnyu)\\b"), 
                              yes = "new york university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(penn state|penn state university|pennsylvania state university|the pennsylvania state university|pennstate)\\b"), 
                              yes = "pennsylvania state university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
  pattern = "\\b(?i)(fred hutchinson cancer research center|fredhutch|fred hutch|fred hutchinson|fred hutchinson center|fred hutch cancer research center)\\b"), 
                              yes = "fred hutchinson cancer research center", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(shanghai jiao tong university|sjtu|jiao tong university|jiao tong)\\b"), 
                              yes = "shanghai jiao tong university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^tsinghua|tsinghua$|tsinghua university$|tsinghua univ$|tsinghua unviersity|tsinghuauniversity|tsinghua_university|tsinghuau)\\b"), 
                              yes = "tsinghua university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^university of michigan|university of michigan$|^the university of michigan|university of michigan, ann arbor)\\b"), 
                              yes = "university of michigan", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^university of virginia|university of virginia$|^uva|uva$)\\b"), 
                              yes = "university of virginia", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^virginia tech|virginia tech$|virginia tech university$|^Virginia Polytechnic)\\b"), 
                              yes = "virginia polytechnic institute and state university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^university of tokyo|^the university of tokyo|university of tokyo$)\\b"), 
                              yes = "university of tokyo", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^university of waterloo|^the university of waterloo|university of waterloo$)\\b"), 
                              yes = "university of waterloo", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^zhejiang|zhejiang university$)\\b"), 
                              yes = "zhejiang university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^university of toronto|university of toronto$)\\b"), 
                              yes = "university of toronto", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^imperial college london|imperial college london$)\\b"), 
                              yes = "imperial college london", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^university of cambridge|university of cambridge$|^cambridge university|cambridge university$)\\b"), 
                              yes = "university of cambridge", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^university of oxford|university of oxford$|^oxford university|oxford university$|^the university of oxford|^university of oxford,)\\b"), 
                              yes = "university of oxford", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^peking university|peking university$|^peking university,)\\b"), 
                              yes = "peking university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^university of southern california|university of southern california$|^university of southern california,)\\b"), 
                              yes = "university of southern california", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^nanjing university|^nanjing univ|nanjing university$|^nanjing university,)\\b"), 
                              yes = "nanjing university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^university of edinburgh|university of edinburgh$|^the university of edinburgh)\\b"), 
                              yes = "university of edinburgh", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^purdue university|^purdue university,|purdue university$|department of statistics,purdue university|purdue univeristy)\\b"), 
                              yes = "purdue university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^university of florida|^university of florida,|university of florida$|universityofflorida)\\b"), 
                              yes = "university of florida", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^university of chicago|^university of chicago,|^the university of chicago|university of chicago$|^uchicago|uchicago$|^u of chicago|u of chicago$)\\b"), 
                              yes = "university of chicago", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^university of illinois|^university of illinois,|^the university of illinois|university of illinois$|university of illinois at chicago|at urbana-champaign$)\\b"), 
                              yes = "university of illinois system", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^national university of singapore|^national university of singapore,|national university of singapore$)\\b"), 
                              yes = "national university of singapore", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^fudan|fudan university$|fudan university)\\b"), 
                              yes = "fudan university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^boston university|boston university$)\\b"), 
                              yes = "boston university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^arizona state|^arizona state,|arizona state university$|arizona state$)\\b"), 
                              yes = "arizona state university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^mcgill|mcgill university$|mcgill$)\\b"), 
                              yes = "mcgill university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^oregon state|^oregon state,|oregon state university$|oregon state$)\\b"), 
                              yes = "oregon state university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^stony brook|stony brook university$|stony brook$|^state university of new york)\\b"), 
                              yes = "state university of new york system", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^university of minnesota|university of minnesota$|^university of minnesota,)\\b"), 
                              yes = "university of minnesota", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^sun yat-sen university|sun yat-sen university$|^sun yat-sen university,)\\b"), 
                              yes = "sun yat-sen university", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(^university of alberta|university of alberta$|^university of alberta,)\\b"), 
                              yes = "university of alberta", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
  pattern = "\\b(?i)(^university of wisconsin-madison|^university of wisconsin|university of wisconsin$|university of wisconsin-madison$|university of wisconsinmadison|^university of wisconsin,|^uw-madison|uw-madison$)\\b"), yes = "university of wisconsin-madison", no = organization)) %>%
  # freelancer, individual, null, etc.
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(freelancer|freelance)\\b"), 
                              yes = "freelancer", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(self|personal|home|private|individual|myself|me|independent|independent contractor)\\b"), 
                              yes = "individual", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(school|university student|a university student|student)\\b"), 
                              yes = "student", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(n/a|none|null|no|na)\\b"),      
                              yes = "none/null", no = organization)) %>% 
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = parentheses),      
                              yes = "none/null", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = ellipses),      
                              yes = "none/null", no = organization)) %>%
  #filter(organization != "none/null") %>% filter(organization != "") %>% filter(organization != "-") %>%
  #filter(organization != "china") %>% filter(organization != "japan") %>%
  group_by(organization) %>% count() %>% arrange(-n) 

organization_counts 

```

```{r editing refusal data}

# getting the totals before refusals 
sum(organization_counts$n)
sum(organization_counts$n) / 2435698

# getting the totals of refusals (none/null) 
organization_counts %>% 
  filter(organization == "none/null"|organization == ""|organization == "-") 
39803+3851+311 # total of all three 

# removing country codes in org code column 
organization_counts %>%
  filter(organization == "china"|organization == "japan")
334+183

```

```{r creating final totals }
# removing refusals and countries from dataset 
organization_counts <- organization_counts %>% 
  filter(organization != "none/null") %>% filter(organization != "") %>% filter(organization != "-") %>% 
  filter(organization != "china") %>% filter(organization != "japan")
  
# i used this snippet of code to search through all of the top-50 academic and top-50 non-academic organizations to catch variations 
# filter(organization_counts, grepl('google', organization))

# this gets the total number and percentage of logins with organization codes 
sum(organization_counts$n)
sum(organization_counts$n) / 2435698

# output to a csv file 
write.csv(organization_counts, "organization_counts.csv")
#saveRDS(company_counts, "company_counts.rds")
```

This suggests that only 15% of the data has valid information in the company column. 

```{r}
users_gh %>% filter(is.na(company))
```

When we look at the logins with missing company data, we can find out more about them on their GitHub profiles. A quick check of these top login sites shows that there is additional information out there in their profiles that we could use to identify sector information. For now, let's just try to categorize what we have. 

# Codifying the Data into Sectors 

The original sectors from the GitHub project in Summer 2019 are business, nonprofit, government, university and individual/private. Let's see if we can get some estimates. 

```{r}

# individual, freelancer or student
individual_counts <- organization_counts %>% 
  filter(grepl('(individual|freelancer|student)', organization))
individual_counts
sum(individual_counts$n)
sum(individual_counts$n) / 2435698
# 8365 or 0.34% 

```

```{r}

# government institutions 
government_counts <- organization_counts %>% 
  filter(grepl('(national laboratory|national institute|national institutes|nih|gov|government|authority|council|department|commission|office|county|administration|.gov$)', organization)) %>% 
  filter(!grepl('(college|university)', organization))
government_counts
sum(government_counts$n)
sum(government_counts$n) / 2435698
# 1409 or 0.05% 

```

```{r}

# nonprofit institutions 
nonprofit_counts <- organization_counts %>% 
  filter(grepl('(?i)association|foundation|fund|board of realtors|assoc.|society|societies|organization|.org$', organization)) %>% 
  filter(!grepl('(geckoboard|moduscreateorg)', organization))
nonprofit_counts
sum(nonprofit_counts$n)
sum(nonprofit_counts$n) / 2435698
# 1830 or 0.07%

```

```{r}

# academic institutions 
academic_counts <- organization_counts %>% 
  filter(grepl('(university|college|institute)', organization))
academic_counts
sum(academic_counts$n)
sum(academic_counts$n) / 2435698
# 30789 or 1.26%

```
```{r}

# businesses 
business_counts <- organization_counts %>% 
  filter(grepl('(?i)(corp|.?com|llp|inc.j|corporation)\\.?$|(lc.|Group|Entertainment|Computing|Software)$|Service.*|Consulting|Consultants|Business|Laboratories|Technologies|Technology|Bank|Company|Studios|Solutions|inc.|l\\.?l\\.?c.?|ltd|employer|Systems|System|Limited|Publishing', organization)) %>% 
  filter(!grepl('(?i)(college|university|institute of technology)', organization))
business_counts
sum(business_counts$n)
sum(business_counts$n) / 2435698
# 

```

```{r}

# non-academic institutions 
other_counts <- organization_counts %>% 
  filter(!grepl('(individual|freelancer|student)', organization)) %>% 
  filter(!grepl('(national laboratory|national institute|national institutes|nih|gov|government|authority|council|department|commission|office|county|administration|.gov$)', organization)) %>% 
  filter(!grepl('(?i)association|foundation|fund|board of realtors|assoc.|society|societies|organization|.org$', organization)) %>%
  filter(!grepl('(university|college|institute)', organization)) %>% 
  filter(!grepl('(?i)(corp|.?com|llp|inc.j|corporation)\\.?$|(lc.|Group|Entertainment|Computing|Software)$|Service.*|Consulting|Consultants|Business|Laboratories|Technologies|Technology|Bank|Company|Studios|Solutions|inc.|l\\.?l\\.?c.?|ltd|employer|Systems|System|Limited|Publishing', organization))
other_counts

# write csvs 
#write.csv(non_academic_counts, "non_academic_counts.csv")
#write.csv(academic_counts, "academic_counts.csv")

```
