---
title: "OSS in the Academic Sector"
description: "This page focuses on classifying GitHub users across all sectors and the business domain."
tags: ["Python","R","text analysis/regex","matching"]
weight: 2
draft: false
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

As part of our overarching strategy for assigning users to specific sectors, we need to be able to assign users to business as well. Given the specifics of our source dataset (GHTorrent), we can reasonably assume that the more frequently that a company name appears, the more "authoratative" (reflective of a consensus) of a representation of that company name it is.  Once we've removed the user entries that correspond to the non-business sectors, we can be reasonably confident in mapping users whose worplace affiliation listing is shared with some critical threshold of other users (i.e. 5) to the business sector.

Lets begin by [obtaining the raw user data from the sql database](https://github.com/DSPG-Young-Scholars-Program/dspg20oss/blob/3a4431544bc32ac6abc82f14f8ccdd9f90923089/ossPy/ossPyFuncs.py#L9), as well as the user mappings for the acadmic and government sector.

```{r pull_data, message = FALSE, results = FALSE, warning = FALSE, echo=FALSE}
rm(list = ls())

# load packages 
for (pkg in c("tidyverse", "igraph", "visNetwork", "data.table", "R.utils", "DT",
              "RPostgreSQL", "cowplot", "maditr", "stringr", "stringi", "gridExtra")) {library(pkg, character.only = TRUE)}

# connect to postgresql to get our data
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# query the users_gh data from github data 
github_users <- dbGetQuery(conn, "SELECT login, email, company FROM gh.ctrs_extra;")

academic <- dbGetQuery(conn, "SELECT login, company_cleaned, is_academic FROM gh.sna_ctr_academic;")
government <- dbGetQuery(conn, "SELECT login, is_gov FROM gh.sna_ctr_gov;")
nonprofit <- dbGetQuery(conn, "SELECT login, is_nonprofit FROM gh.sna_ctr_nonprofits;")

# disconnect from postgresql database 
dbDisconnect(conn)

# joining the datasets 
combined_user_data <- github_users %>% 
  full_join(academic, by = "login") %>% 
  mutate(is_academic = replace_na(is_academic, 0))

combined_user_data <- combined_user_data %>% 
  full_join(government, by = "login") %>% 
  mutate(is_gov = replace_na(is_gov, 0))

combined_user_data <- combined_user_data %>% 
  full_join(nonprofit, by = "login") %>% 
  mutate(is_nonprofit = replace_na(is_nonprofit, 0))

# household 
household <- read.csv("/sfs/qumulo/qhome/kb7hp/git/dspg20oss/ossPy/keyFiles/individualKeys.csv", header=FALSE)
household <- household %>% 
  rename(strings = V1) %>% 
  mutate(strings = as.character(strings))
household$strings <- substring(household$strings, 2)
household$strings <- substr(household$strings,1, nchar(household$strings)-1)

combined_user_data <- combined_user_data %>% 
  mutate(is_household = ifelse(test = str_detect(string = company, 
         pattern = paste(c("\\b(?i)(z3x", na.omit(household$strings), 
         "z3x|self-employed|unemployed|available for hire)\\b"), collapse = "|")), 
         yes = TRUE, no = NA)) %>% 
  mutate(is_household = replace_na(is_household, 0))

# null values 
null_values <- read.csv("/sfs/qumulo/qhome/kb7hp/git/dspg20oss/ossPy/keyFiles/nullKeys.csv", header=FALSE)
null_values <- null_values %>% 
  rename(strings = V1) %>% 
  mutate(strings = as.character(strings))
null_values$strings <- substring(null_values$strings, 2)
null_values$strings <- substr(null_values$strings,1, nchar(null_values$strings)-1)

combined_user_data <- combined_user_data %>% 
  mutate(is_nullvalue = ifelse(test = str_detect(string = company, 
         pattern = paste(c("\\b(?i)(z3x", na.omit(null_values$strings), "z3x)\\b"), collapse = "|")), 
         yes = TRUE, no = NA)) %>% 
  mutate(is_nullvalue = replace_na(is_nullvalue, 0)); combined_user_data

# implementing daniel's approaches 
legal_entities <- read.csv("/sfs/qumulo/qhome/kb7hp/git/dspg20oss/ossPy/keyFiles/curatedLegalEntitesRaw.csv", header=FALSE)
legal_entities <- legal_entities %>% 
  rename(strings = V1) %>% 
  mutate(strings = as.character(strings))
legal_entities$strings <- substring(legal_entities$strings, 2)
legal_entities$strings <- substr(legal_entities$strings,1, nchar(legal_entities$strings)-1)

symbol_strings <- read.csv("/sfs/qumulo/qhome/kb7hp/git/dspg20oss/ossPy/keyFiles/symbolRemove.csv", header=FALSE)
symbol_strings <- symbol_strings %>% 
  rename(strings = V1) %>% 
  mutate(strings = as.character(strings))
symbol_strings$strings <- substring(symbol_strings$strings, 2)
symbol_strings$strings <- substr(symbol_strings$strings,1, nchar(symbol_strings$strings)-1)
symbol_strings <- symbol_strings %>% slice(-17:-20)

curated_domains <- read.csv("/sfs/qumulo/qhome/kb7hp/git/dspg20oss/ossPy/keyFiles/curatedDomains.csv", header=FALSE)
curated_domains <- curated_domains %>% 
  rename(strings = V1) %>% 
  mutate(strings = as.character(strings))
curated_domains$strings <- substring(curated_domains$strings, 2)
curated_domains$strings <- substr(curated_domains$strings,1, nchar(curated_domains$strings)-1)

combined_user_data <- combined_user_data %>% 
  mutate(company_original = company) %>%
  mutate(company = str_replace_all(company, paste(c("(?i)(zqx", na.omit(legal_entities$strings), 
                                                    "zqx|, Inc.)"), collapse = "|"), "")) %>% 
  mutate(company = str_replace_all(company, paste(c("(?i)(zqx", na.omit(symbol_strings$strings), 
                                                    ", $|,$|zqx)"), collapse = "|"), "")) %>%
  mutate(company = str_replace_all(company, paste(c("(?i)(zqx", na.omit(curated_domains$strings), 
                                                    "zqx)"), collapse = "|"), "")) %>%
  mutate(company = tolower(company)); combined_user_data
  #filter(grepl(".br", company_original)) %>% 
  #select(company, company_original)

#### additional cleaning steps 
potential_business <- combined_user_data %>%
  select(-company_cleaned, -company_original) %>% 
  filter(is_academic == 0 & is_gov == 0 & is_nonprofit == 0 & is_household == 0 & is_nullvalue == 0) %>% 
  filter(company != "china" & company != "japan" & company != "none" & company != "no"); potential_business 

company_totals <- potential_business %>% 
  group_by(company) %>% 
  count() %>% 
  arrange(-n)# %>% filter(grepl("microsoft", company))

# this bit classifies an additional 6,000 academic developers 
new_academic_list <- company_totals %>% 
  filter(grepl("university|college", company)) %>% 
  filter(n > 1) %>% 
  rename(institutions = company); new_academic_list

combined_user_data <- combined_user_data %>% 
  mutate(new_academic = ifelse(test = str_detect(string = company, 
         pattern = paste(c("\\b(?i)(z3x", na.omit(new_academic_list$institutions), "z3x)\\b"), collapse = "|")), 
         yes = TRUE, no = NA)) %>% 
  mutate(new_academic = replace_na(new_academic, 0))

potential_business <- combined_user_data %>%
  filter(is_academic == 0 & is_gov == 0 & is_nonprofit == 0 & is_household == 0 & is_nullvalue == 0 & new_academic == 0) %>% 
  filter(company != "china" & company != "japan" & company != "none" & company != "no"); potential_business 
  #%>% drop_na(email)

company_totals <- potential_business %>% 
  group_by(company) %>% 
  count(company) %>% 
  arrange(-n) %>% 
  filter(n != 4601) %>% 
  rename(total = n) ; company_totals# %>% filter(grepl("microsoft", company))

business <- combined_user_data %>% 
  full_join(company_totals, by = "company") %>% 
  select(login, company, total) %>% 
  filter(total > 5) %>% 
  select(-total, -company) %>% 
  mutate(is_business = 1) 

combined_user_data <- combined_user_data %>% 
  full_join(business, by = "login") %>% 
  mutate(is_business = replace_na(is_business, 0))

combined_user_data %>% 
  filter(is_academic == 1 | new_academic == 1) %>% 
  count()

combined_user_data %>% 
  filter(is_gov == 1) %>%
  count()

combined_user_data %>% 
  filter(is_nonprofit == 1) %>%
  count()

combined_user_data %>% 
  filter(is_household == 1) %>%
  count()

combined_user_data %>% 
  filter(is_business == 1) %>%
  count()

final_counts <- data.frame(sector = as.factor(c("business", "academic","houshold","government", "nonprofit")),
                           total = as.numeric(c("115893", "46403", "5455", "3576", "823")))

positions <- c("business", "academic","houshold","government", "nonprofit")
```

```{r, fig.height = 7, fig.width=12}
ggplot(data=final_counts, aes(x=sector, y=total)) +
  geom_bar(stat="identity",  fill = c("#232D4B", "#E57200", "#D9E12B", "#0E879C", "#E6A01D")) +
  scale_x_discrete(limits = positions) +
  theme_minimal() +
  theme(plot.title = element_text(size=23, hjust = 0.45),
        axis.text.y = element_text(size = 16),
        axis.text.x = element_text(size = 16),
        axis.title =element_text(size=18),
        axis.title.x=element_blank()) +
  labs(y = "Total GitHub Users within Sector") +
  ggtitle("Total GitHub Users Classified by Economic Sector")
```

```{r, echo=FALSE, fig.height = 7, fig.width=12}

top20companies <- company_totals %>% 
  filter(total > 399)

company_positions <- data.frame(company = c("microsoft", "google","red hat", "ibm", "facebook",
                                                 "intel", "thoughtworks","alibaba","tencent", "amazon",
                                                 "baidu", "esri","sap","shopify", "mozilla",
                                                 "pivotal", "oracle","salesforce","yandex", "linkedin"), 
                                   countries = as.factor(c("usa","usa","usa","usa","usa",
                                                 "usa","usa","china","china","usa",
                                                 "china", "usa", "germany", "canada", "usa",
                                                 "usa","usa","usa","russia","usa"))) 
top20companies <- top20companies %>% 
  full_join(company_positions, by = "company")

top20companies$company <- fct_relevel(top20companies$company, "microsoft", "google","red hat", "ibm", "facebook",
                                                 "intel", "thoughtworks","alibaba","tencent", "amazon",
                                                 "baidu", "esri","sap","shopify", "mozilla",
                                                 "pivotal", "oracle","salesforce","yandex", "linkedin")
 
ggplot(top20companies) +
  geom_point(aes(x = company, y = total, colour = countries), size = 4) +
  geom_segment( aes(x=company, xend=company, y=0, yend=total)) +
  #ggtitle("Most Prominent Businesses\nDeveloping OSS (By GitHub Users)") +
  coord_flip() +
  theme_minimal() +
  scale_color_manual(labels=c("canada", "china",   "germany", "russia", "usa"),
                     values=c("#ADD8E6", "#232D4B", "#0E879C",  "#D9E12B", "#E57200")) +
  theme(plot.title = element_text(size=23, hjust = 0.5),
        #axis.title.x=element_blank(),
        axis.title =element_text(size=18),
        axis.title.y =element_blank(),
        #axis.text.x = element_text(size = 18),
        axis.text.y = element_text(size = 16),
        axis.text.x = element_text(size = 16),
        legend.title=element_text(size=18, hjust = 0.5, face="bold"),
        legend.text=element_text(size=18),
        legend.position = c(.9, .6),
        legend.justification = c("right", "bottom"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6),
        legend.background = element_rect(fill="white",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) +
  labs(y = "Total GitHub Users", title = "Most Prominent Businesses\nDeveloping OSS (By GitHub Users)") 
```





