---
title: "International Contributor Networks: Cumulative Stats"
author: "Brandon L. Kramer"
output: html_document
---

## Loading Data 

We used this code to pull data for the construction of Github network data (cumulatively.

```{r loading edgelist data, warning=FALSE, echo=FALSE}
rm(list = ls())
# install.packages(c("tidyverse", "igraph", "visNetwork", "bc3net", 
# "data.table", "R.utils", "RPostgreSQL", "cowplot", "maditr", "linkprediction", "poweRlaw"))

# load packages 
for (pkg in c("tidyverse", "igraph", "visNetwork", "bc3net", "data.table", "R.utils", "RPostgreSQL",
              "cowplot", "maditr", "lubridate", "linkprediction", "poweRlaw")) {library(pkg, character.only = TRUE)}

# connect to postgresql to get data (in rivanna)
conn <- dbConnect(drv = PostgreSQL(), dbname = "sdad_data", 
                  host = "sdad.policy-analytics.net", port = 5436, 
                  user = Sys.getenv("db_userid"), password = Sys.getenv("db_pwd"))

# query the bipartite edgelist data from github data  
bp_edgelist <- dbGetQuery(conn, "SELECT login, slug, year, weight 
                                 FROM github.intl_dyn_bp_edges 
                                 WHERE year > 2007 AND year < 2011")
                                 #WHERE year > 2007 AND year < 2012")
                                 #WHERE year > 2007 AND year < 2013")
                                 #WHERE year > 2007 AND year < 2014")
                                 #WHERE year > 2007 AND year < 2015")
                                 #WHERE year > 2007 AND year < 2016")
                                 #WHERE year > 2007 AND year < 2017")
                                 #WHERE year > 2007 AND year < 2018")
                                 #WHERE year > 2007 AND year < 2019")
                                 #WHERE year = 2008")
                                 #WHERE year > 2007 AND year < 2010")

# disconnect from postgresql
dbDisconnect(conn)
```

## Constructing Single Mode Contributor Networks 

In this snippet of code, we transpose the original bipartite networks into single mode networks. In this case, those single mode networks are only composed of contributors. These steps include (1) creating a biadjacency matrix of contributors and repos, (2) transposing the biadjacency matrix into a regular adjacency matrix of just contributors,  (3) creating a network from that matrix, and (4) removing any of the loops. At each step, I create a start and end time stamp so we know how long these processes take and whether we need to take another approach for calculating certain statistics. 

```{r network stats}
# in this snippet, we will be logging start/end times 
mat_start <- data.frame(event="mat_start", time=now("EST"))

# this code is taken from network scientists to reduce bipartite networks to single mode networks 
bp_matrix <- spMatrix(nrow=length(unique(bp_edgelist$login)),
              ncol=length(unique(bp_edgelist$slug)),
              i = as.numeric(factor(bp_edgelist$login)),
              j = as.numeric(factor(bp_edgelist$slug)),
              x = rep(1, length(as.numeric(bp_edgelist$login))))
row.names(bp_matrix) <- levels(factor(bp_edgelist$login))
colnames(bp_matrix) <- levels(factor(bp_edgelist$slug))
#rm(bp_edgelist) # trying to minimize weight on RAM 

# logging the times and saving the work in RDS files 
mat_end <- data.frame(event="mat_end", time=now("EST"))
time_log <- rbind(mat_start, mat_end); rm(mat_start, mat_end)
#saveRDS(bp_matrix, "bp_matrix.rds")
saveRDS(time_log, "time_log.rds")

# logging the times 
mm_start <- data.frame(event="mm_start", time=now("EST"))
time_log <- rbind(time_log, mm_start)

# we then multiply these incidence matrices and impute zeroes to prevent self loops 
login_matrix <- tcrossprod(bp_matrix)
diag(login_matrix) <- 0
rm(bp_matrix)

# logging the times and saving the work in RDS files 
mm_end <- data.frame(event="mm_end", time=now("EST"))
time_log <- rbind(time_log, mm_end); rm(mm_start, mm_end)
#saveRDS(login_matrix, "login_matrix.rds")
saveRDS(time_log, "time_log.rds")

# convert it into a network and removing the loops 
net_start <- data.frame(event="net_start", time=now("EST"))
time_log <- rbind(time_log, net_start); rm(net_start)
login_network <- graph_from_adjacency_matrix(login_matrix, mode = "undirected", weighted = TRUE)
login_network <- simplify(login_network, remove.loops = TRUE)

# logging the times and saving the work in RDS files 
net_end <- data.frame(event="net_end", time=now("EST"))
time_log <- rbind(time_log, net_end); rm(net_end)
#saveRDS(login_network, "login_network.rds")
saveRDS(time_log, "time_log.rds")
```

## Calculating Global Network Statistics 

In this snippet, we calculate various network statistics at the global level of the network, including the node count, edge count, the number of commits, the network density, transitivity, and modularity. These were all calculated using the standard function in R's igraph package with the only exception being that we calculated the modularity with the Louvain method (Blondel et al. 2008). As we went through and calculated the statistics for each network, we ran into a number of computational challenges. While a standard laptop computer will suffice to run the original few networks, we ultimately migrated to an instance (i.e. UVA's Rivanna supercomputing platform) to calculate these statistics. Even then, we ultimately ended up not running the diameter measures for 2014-2018 or the mean distance for 2016-2018 because of our own time limitations and lack of patience. We will likely come back to calculate these measures at a later date, but for now we decided to allocate our efforts elsewhere. We also used this code to construct node-level statistics for the cumulative networks, including the degree centrality measure (both weight and unweighted), the k-core measure, the Louvain cluster grouping, and the component grouping.

```{r global network stats}
# loading the network (if the instance crashes while doing network_stats)
#login_network <- readRDS("login_network.rds")
#time_log <- readRDS("time_log.rds")
net_stats_start <- data.frame(event="net_stats_start", time=now("EST"))
time_log <- rbind(time_log, net_stats_start); rm(net_stats_start)
network_stats <- data.frame(year="2008-10")                                          

# node and edge counts  
network_stats$node_count <- gorder(login_network)  
network_stats$edge_count <- gsize(login_network)
network_stats$commits <- sum(bp_edgelist$weight)

# isolates, dyads and triads 
network_stats$isolates <- sum(degree(login_network)==0)
network_stats$dyads <- dyad_census(login_network)[1]
oss_triads <- triad_census(login_network)
network_stats$triads_003 <- oss_triads[1] 
network_stats$triads_102 <- oss_triads[3]
network_stats$triads_201 <- oss_triads[11]
network_stats$triads_300 <- oss_triads[16]
net_counts <- data.frame(event="net_counts", time=now("EST"))
time_log <- rbind(time_log, net_counts); rm(net_counts, oss_triads)

# density and transitivity
network_stats$density <- edge_density(login_network, loops=FALSE) 
network_stats$transitivity <- transitivity(login_network)
net_globals <- data.frame(event="net_globals", time=now("EST"))
time_log <- rbind(time_log, net_globals); rm(net_globals)

# diameter and mean distance (very computationally intensive)
#network_stats$diameter <- diameter(login_network)
#network_stats$mean_distance <- mean_distance(login_network, directed=FALSE)

# community detection (using louvain method)
louvain <- cluster_louvain(login_network)
network_stats$louvain <- modularity(louvain)
network_stats$louvain_scaled <- modularity(louvain) / gorder(login_network)
network_stats$louvain_logged <- modularity(louvain) / log(gorder(login_network))
# community detection (using fast & greedy method)
fstgrdy <- fastgreedy.community(login_network)
network_stats$fstgrdy <- modularity(louvain)
network_stats$fstgrdy_scaled <- modularity(louvain) / gorder(login_network)
network_stats$fstgrdy_logged <- modularity(louvain) / log(gorder(login_network))

# decomposition statistics 
decomposition_stats <- table(sapply(decompose.graph(login_network), vcount))

net_comm_det <- data.frame(event="net_comm_det", time=now("EST"))
time_log <- rbind(time_log, net_comm_det); rm(net_comm_det)

# now, we need to construct a nodelist 
nodelist <- data.frame(id = c(1:(igraph::vcount(login_network))), login = igraph::V(login_network)$name)

# degree, weighted degree, k core and modularity 
node_stats_start <- data.frame(event="node_stats_start", time=now("EST"))
time_log <- rbind(time_log, node_stats_start); rm(node_stats_start)
nodelist$degree <- degree(login_network)
nodelist$wtd_degree <- strength(login_network)
nodelist$k_core <- coreness(login_network)
#louvain <- cluster_louvain(login_network)
nodelist$louvain_comm <- louvain$membership
#fstgrdy <- fastgreedy.community(login_network)
nodelist$fstgrdy_comm <- fstgrdy$membership
components <- components(login_network)
nodelist$component <- components$membership

node_stats_end <- data.frame(event="node_stats_end", time=now("EST"))
time_log <- rbind(time_log, node_stats_end); rm(node_stats_end, louvain, components)

setwd("~/oss-2020/src/international-network-analysis/intl-dyn-ctr-nets-cum")
saveRDS(network_stats, "global_netstats_2008-10.rds")  
saveRDS(decomposition_stats, "decomposition_stats_2008-10.rds") 
saveRDS(nodelist, "nodelist_2008-10.rds")  
saveRDS(time_log, "timelog_2008-10.rds")              
```

## Aggregating Statistics 

Once we got those statistics calculated, we aggregated them together using this code chunk. 

```{r concatenating global_netstats_cum}

setwd("~/oss-2020/src/international-network-analysis/intl-dyn-ctr-nets-cum")
#setwd("~/2008")
global_netstats_2008 <- readRDS("global_netstats_2008.rds")
#setwd("~/2008-09")
global_netstats_200809 <- readRDS("global_netstats_2008-09.rds")
#setwd("~/2008-10")
global_netstats_200810 <- readRDS("global_netstats_2008-10.rds")
#setwd("~/2008-11")
global_netstats_200811 <- readRDS("global_netstats_2008-11.rds")
#setwd("~/2008-12")
global_netstats_200812 <- readRDS("global_netstats_2008-12.rds")
#setwd("~/2008-13")
global_netstats_200813 <- readRDS("global_netstats_2008-13.rds")
#setwd("~/2008-14")
global_netstats_200814 <- readRDS("global_netstats_2008-14.rds")
#setwd("~/2008-15")
global_netstats_200815 <- readRDS("global_netstats_2008-15.rds")
#setwd("~/2008-16")
global_netstats_200816 <- readRDS("global_netstats_2008-16.rds")
#setwd("~/2008-17")
global_netstats_200817 <- readRDS("global_netstats_2008-17.rds")
#setwd("~/2008-18")
global_netstats_200818 <- readRDS("global_netstats_2008-18.rds")

global_netstats_cum <- rbind(global_netstats_2008, global_netstats_200809)

global_netstats_cum <- rbind(global_netstats_2008, global_netstats_200809, global_netstats_200810, global_netstats_200811, global_netstats_200812, 
                         global_netstats_200813, global_netstats_200814, global_netstats_200815, global_netstats_200816, global_netstats_200817, global_netstats_200818)

global_netstats_cum <- as_tibble(c("2008", "2008-09", "2008-10", "2008-11", "2008-12", "2008-13", "2008-14", "2008-15", "2008-16", "2008-17", "2008-18")) %>% 
  bind_cols(global_netstats_cum) %>% # select(-year) %>% 
  rename(year_cum = value)

saveRDS(global_netstats_cum, "global_netstats_cum.rds") 

rm(global_netstats_2008, global_netstats_200809, global_netstats_200810, global_netstats_200811, global_netstats_200812, 
   global_netstats_200813, global_netstats_200814, global_netstats_200815, global_netstats_200816, global_netstats_200817, global_netstats_200818)

```

And then aggregated them together into one file. 

```{r binding cum nodelists}
# read nodelists
rm(list = ls())
setwd("~/oss_networks_cum/2008")
nodelist_2008 <- readRDS("nodelist_2008.rds")
setwd("~/oss_networks_cum/2008-09")
nodelist_200809 <- readRDS("nodelist_2008_09.rds")
setwd("~/oss_networks_cum/2008-10")
nodelist_200810 <- readRDS("nodelist_2008_10.rds")
setwd("~/oss_networks_cum/2008-11")
nodelist_200811 <- readRDS("nodelist_2008_11.rds")
setwd("~/oss_networks_cum/2008-12")
nodelist_200812 <- readRDS("nodelist_2008_12.rds")
setwd("~/oss_networks_cum/2008-13")
nodelist_200813 <- readRDS("nodelist_2008_13.rds")
setwd("~/oss_networks_cum/2008-14")
nodelist_200814 <- readRDS("nodelist_2008_14.rds")
setwd("~/oss_networks_cum/2008-15")
nodelist_200815 <- readRDS("nodelist_2008_15.rds")
setwd("~/oss_networks_cum/2008-16")
nodelist_200816 <- readRDS("nodelist_2008_16.rds")
setwd("~/oss_networks_cum/2008-17")
nodelist_200817 <- readRDS("nodelist_2008_17.rds")
setwd("~/oss_networks_cum/2008-18")
nodelist_200818 <- readRDS("nodelist_2008_18.rds")

full_nodelist <- nodelist_2008 %>% 
  select(-id) %>% 
  mutate(login = as.character(login)) %>% 
  rename(deg08 = degree,
         wtddeg08 = wtd_degree, 
         kcore08 = k_core,
         louvain08 = louvain_comm,
         comp08 = component) %>%     
  right_join(nodelist_200809, by = "login") %>% 
  select(-id) %>% 
  rename(deg0809 = degree,
         wtddeg0809 = wtd_degree, 
         kcore0809 = k_core,
         louvain0809 = louvain_comm,
         comp0809 = component) %>% 
  right_join(nodelist_200810, by = "login") %>% 
  select(-id) %>% 
  rename(deg0810 = degree,
         wtddeg0810 = wtd_degree, 
         kcore0810 = k_core,
         louvain0810 = louvain_comm,
         comp0810 = component) %>% 
  right_join(nodelist_200811, by = "login") %>% 
  select(-id) %>% 
  rename(deg0811 = degree,
         wtddeg0811 = wtd_degree, 
         kcore0811 = k_core,
         louvain0811 = louvain_comm,
         comp0811 = component) %>% 
  right_join(nodelist_200812, by = "login") %>% 
  select(-id) %>% 
  rename(deg0812 = degree,
         wtddeg0812 = wtd_degree, 
         kcore0812 = k_core,
         louvain0812 = louvain_comm,
         comp0812 = component) %>% 
  right_join(nodelist_200813, by = "login") %>% 
  select(-id) %>% 
  rename(deg0813 = degree,
         wtddeg0813 = wtd_degree, 
         kcore0813 = k_core,
         louvain0813 = louvain_comm,
         comp0813 = component) %>% 
  right_join(nodelist_200814, by = "login") %>% 
  select(-id) %>% 
  rename(deg0814 = degree,
         wtddeg0814 = wtd_degree, 
         kcore0814 = k_core,
         louvain0814 = louvain_comm,
         comp0814 = component) %>% 
  right_join(nodelist_200815, by = "login") %>% 
  select(-id) %>% 
  rename(deg0815 = degree,
         wtddeg0815 = wtd_degree, 
         kcore0815 = k_core,
         louvain0815 = louvain_comm,
         comp0815 = component) %>% 
  right_join(nodelist_200816, by = "login") %>% 
  select(-id) %>% 
  rename(deg0816 = degree,
         wtddeg0816 = wtd_degree, 
         kcore0816 = k_core,
         louvain0816 = louvain_comm,
         comp0816 = component) %>% 
  right_join(nodelist_200817, by = "login") %>% 
  select(-id) %>% 
  rename(deg0817 = degree,
         wtddeg0817 = wtd_degree, 
         kcore0817 = k_core,
         louvain0817 = louvain_comm,
         comp0817 = component) %>% 
  right_join(nodelist_200818, by = "login") %>% 
  select(-id) %>% 
  rename(deg0818 = degree,
         wtddeg0818 = wtd_degree, 
         kcore0818 = k_core,
         louvain0818 = louvain_comm,
         comp0818 = component) 

setwd("~/oss_networks_cum")
saveRDS(full_nodelist, "full_nodelist_cum.rds")
```

```{r}

table <- as.data.frame(readRDS("decomposition_stats_2008.rds"))
table <- t(table)

```


##################################################### 
#####################################################
##################################################### NOT DONE YET 
#####################################################
#####################################################

## Calculating Power Laws Based on Degree Distribution of Networks (Not Done)

```{r fitting power laws}
power_law_start <- data.frame(event="power_law_start", time=now("EST"))
time_log <- rbind(time_log, power_law_start); rm(power_law_start)

data <- nodelist$degree
data.dist <- data.frame(k=0:max(data),p_k=degree_distribution(login_network))
data.dist <- data.dist[data.dist$p_k>0,]
ggplot(data.dist) + geom_point(aes(x=k, y=p_k)) + theme_bw()

m_pl <- displ$new(data)
est_pl <- estimate_xmin(m_pl)
est_pl$xmin # initial estimation of kmin 
est_pl$pars # initial estimation of γ
est_pl$gof # calculate D with Kolgomorov-Smirnov test

# finish remainder of process using https://rpubs.com/lgadar/power-law

power_law_end <- data.frame(event="power_law_end", time=now("EST"))
time_log <- rbind(time_log, power_law_end); rm(power_law_end)
```

## Normalizing Degree Distribributions with Cosine Similarity Scores (Not Done Yet)

```{r normalizing networks}
cos_norm <- proxfun(login_network, method="cos", value="edgelist") %>% 
  filter(from < to) %>% 
  rename(cos_norm = value)
```

## Testing for Assortativity and Homophily (Not Done Yet)

```{r testing patterns in assortativity and homophily}
# connect to postgresql to get data (in rivanna)
conn <- dbConnect(drv = PostgreSQL(), dbname = "sdad_data", 
                  host = "sdad.policy-analytics.net", port = 5436, 
                  user = Sys.getenv("db_userid"), password = Sys.getenv("db_pwd"))

# query the bipartite edgelist data from github data  
node_attributes <- dbGetQuery(conn, "SELECT name, country_code_vis
                                 FROM github.intl_st_bp_nodes")
# disconnect from postgresql
dbDisconnect(conn); rm(conn)

# adding country codes to the nodelist 
nodelist <- dplyr::full_join(nodelist, node_attributes, by = c("nName" = "login")) %>% 
  dplyr::mutate(new_col = ifelse(test = is.na(x = country_code), yes = paste("repo"), no = country_code)) %>% 
  dplyr::select(-country_code) %>% 
  dplyr::rename(name = nName, country_code = new_col)

# testing homophily based on country_code
assortativity_nominal(net, V(net)$media.type, directed=F)

# using linkprediction to test for structural homophily 



```

## References 

Blondel, V. D., Guillaume, J. L., Lambiotte, R., & Lefebvre, E. (2008). Fast unfolding of communities in large networks. Journal of statistical mechanics: theory and experiment, 2008(10), P10008.

http://pablobarbera.com/big-data-upf/html/02b-networks-descriptive-analysis.html
https://igraph.org/r/doc/cluster_louvain.html
https://kateto.net/networks-r-igraph 
https://sites.fas.harvard.edu/~airoldi/pub/books/BookDraft-CsardiNepuszAiroldi2016.pdf
https://rpubs.com/lgadar/power-law 
http://recon.icm.edu.pl/wp-content/uploads/2019/05/linkprediction.pdf


































