---
title: "OSS in the Academic Sector"
description: "This page focuses on classifying GitHub users across all sectors and the business domain."
tags: ["Python","R","text analysis/regex","matching"]
weight: 2
draft: false
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

As part of our overarching strategy for assigning users to specific sectors, we need to be able to assign users to business as well. Given the specifics of our source dataset (GHTorrent), we can reasonably assume that the more frequently that a company name appears, the more "authoratative" (reflective of a consensus) of a representation of that company name it is.  Once we've removed the user entries that correspond to the non-business sectors, we can be reasonably confident in mapping users whose worplace affiliation listing is shared with some critical threshold of other users (i.e. 5) to the business sector.

Lets begin by [obtaining the raw user data from the sql database](https://github.com/DSPG-Young-Scholars-Program/dspg20oss/blob/3a4431544bc32ac6abc82f14f8ccdd9f90923089/ossPy/ossPyFuncs.py#L9), as well as the user mappings for the acadmic and government sector.

```{r pull_data, message = FALSE, results = FALSE, warning = FALSE, echo=FALSE}
rm(list = ls())

# load packages 
for (pkg in c("tidyverse", "igraph", "visNetwork", "data.table", "R.utils", "DT",
              "RPostgreSQL", "cowplot", "maditr", "stringr", "stringi", "gridExtra")) {library(pkg, character.only = TRUE)}

# connect to postgresql to get our data
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# query the users_gh data from github data 
github_users <- dbGetQuery(conn, "SELECT login, email, company FROM gh.ctrs_extra;")

academic <- dbGetQuery(conn, "SELECT login, institution, country, is_academic FROM gh.sna_ctr_academic;")
government <- dbGetQuery(conn, "SELECT login, is_gov FROM gh.sna_ctr_gov;")
nonprofit <- dbGetQuery(conn, "SELECT login, is_nonprofit FROM gh.sna_ctr_nonprofits;")

# disconnect from postgresql database 
dbDisconnect(conn)

# joining the datasets 
combined_user_data <- github_users %>% 
  full_join(academic, by = "login") %>% 
  mutate(is_academic = replace_na(is_academic, 0))

combined_user_data <- combined_user_data %>% 
  full_join(government, by = "login") %>% 
  mutate(is_gov = replace_na(is_gov, 0))

combined_user_data <- combined_user_data %>% 
  full_join(nonprofit, by = "login") %>% 
  mutate(is_nonprofit = replace_na(is_nonprofit, 0))

# household 
household <- read.csv("/sfs/qumulo/qhome/kb7hp/git/dspg20oss/ossPy/keyFiles/individualKeys.csv", header=FALSE)
household <- household %>% 
  rename(strings = V1) %>% 
  mutate(strings = as.character(strings))
household$strings <- substring(household$strings, 2)
household$strings <- substr(household$strings,1, nchar(household$strings)-1)

combined_user_data <- combined_user_data %>% 
  mutate(is_household = ifelse(test = str_detect(string = company, 
         pattern = paste(c("\\b(?i)(z3x", na.omit(household$strings), 
         "z3x|self-employed|unemployed|available for hire)\\b"), collapse = "|")), 
         yes = TRUE, no = NA)) %>% 
  mutate(is_household = replace_na(is_household, 0))

# null values 
null_values <- read.csv("/sfs/qumulo/qhome/kb7hp/git/dspg20oss/ossPy/keyFiles/nullKeys.csv", header=FALSE)
null_values <- null_values %>% 
  rename(strings = V1) %>% 
  mutate(strings = as.character(strings))
null_values$strings <- substring(null_values$strings, 2)
null_values$strings <- substr(null_values$strings,1, nchar(null_values$strings)-1)

combined_user_data <- combined_user_data %>% 
  mutate(is_nullvalue = ifelse(test = str_detect(string = company, 
         pattern = paste(c("\\b(?i)(z3x", na.omit(null_values$strings), "z3x)\\b"), collapse = "|")), 
         yes = TRUE, no = NA)) %>% 
  mutate(is_nullvalue = replace_na(is_nullvalue, 0)); combined_user_data

# implementing daniel's approaches 
legal_entities <- read.csv("/sfs/qumulo/qhome/kb7hp/git/dspg20oss/ossPy/keyFiles/curatedLegalEntitesRaw.csv", header=FALSE)
legal_entities <- legal_entities %>% 
  rename(strings = V1) %>% 
  mutate(strings = as.character(strings))
legal_entities$strings <- substring(legal_entities$strings, 2)
legal_entities$strings <- substr(legal_entities$strings,1, nchar(legal_entities$strings)-1)

symbol_strings <- read.csv("/sfs/qumulo/qhome/kb7hp/git/dspg20oss/ossPy/keyFiles/symbolRemove.csv", header=FALSE)
symbol_strings <- symbol_strings %>% 
  rename(strings = V1) %>% 
  mutate(strings = as.character(strings))
symbol_strings$strings <- substring(symbol_strings$strings, 2)
symbol_strings$strings <- substr(symbol_strings$strings,1, nchar(symbol_strings$strings)-1)
symbol_strings <- symbol_strings %>% slice(-17:-20)

curated_domains <- read.csv("/sfs/qumulo/qhome/kb7hp/git/dspg20oss/ossPy/keyFiles/curatedDomains.csv", header=FALSE)
curated_domains <- curated_domains %>% 
  rename(strings = V1) %>% 
  mutate(strings = as.character(strings))
curated_domains$strings <- substring(curated_domains$strings, 2)
curated_domains$strings <- substr(curated_domains$strings,1, nchar(curated_domains$strings)-1)

combined_user_data <- combined_user_data %>% 
  mutate(company_original = company) %>%
  mutate(company = str_replace_all(company, paste(c("(?i)(zqx", na.omit(legal_entities$strings), 
                                                    "zqx|, Inc.)"), collapse = "|"), "")) %>% 
  mutate(company = str_replace_all(company, paste(c("(?i)(zqx", na.omit(symbol_strings$strings), 
                                                    ", $|,$|zqx)"), collapse = "|"), "")) %>%
  mutate(company = str_replace_all(company, paste(c("(?i)(zqx", na.omit(curated_domains$strings), 
                                                    "zqx)"), collapse = "|"), "")) %>%
  mutate(company = tolower(company)); combined_user_data
  #filter(grepl(".br", company_original)) %>% 
  #select(company, company_original)

#### additional cleaning steps 
potential_business <- combined_user_data %>%
  select(-company_original) %>% 
  filter(is_academic == 0 & is_gov == 0 & is_nonprofit == 0 & is_household == 0 & is_nullvalue == 0) %>% 
  filter(company != "china" & company != "japan" & company != "none" & company != "no"); potential_business 

company_totals <- potential_business %>% 
  group_by(company) %>% 
  count() %>% 
  arrange(-n)# %>% filter(grepl("microsoft", company))

# this bit classifies an additional 6,000 academic developers 
new_academic_list <- company_totals %>% 
  filter(grepl("university|college", company)) %>% 
  filter(n > 1) %>% 
  rename(institutions = company); new_academic_list

combined_user_data <- combined_user_data %>% 
  mutate(new_academic = ifelse(test = str_detect(string = company, 
         pattern = paste(c("\\b(?i)(z3x", na.omit(new_academic_list$institutions), "z3x)\\b"), collapse = "|")), 
         yes = TRUE, no = NA)) %>% 
  mutate(new_academic = replace_na(new_academic, 0))

potential_business <- combined_user_data %>%
  filter(is_academic == 0 & is_gov == 0 & is_nonprofit == 0 & is_household == 0 & is_nullvalue == 0 & new_academic == 0) %>% 
  filter(company != "china" & company != "japan" & company != "none" & company != "no"); potential_business 
  #%>% drop_na(email)

company_totals <- potential_business %>% 
  group_by(company) %>% 
  count(company) %>% 
  arrange(-n) %>% 
  filter(n != 4601) %>% 
  rename(total = n) ; company_totals# %>% filter(grepl("microsoft", company))

business <- combined_user_data %>% 
  full_join(company_totals, by = "company") %>% 
  select(login, company, total) %>% 
  filter(total > 5) %>% 
  select(-total, -company) %>% 
  mutate(is_business = 1) 

combined_user_data <- combined_user_data %>% 
  full_join(business, by = "login") %>% 
  mutate(is_business = replace_na(is_business, 0))

classified_users <- combined_user_data %>% 
  rename(is_null = is_nullvalue) %>% 
  mutate(is_null = ifelse(is.na(company), 1, is_null)) %>% 
  mutate(sector = ifelse(test = str_detect(string = is_null, pattern = "1"), yes = "null/missing", no = "not classified"),
         
         sector = ifelse(test = str_detect(string = is_household, pattern = "1"), yes = "household", no = sector),
         # this corrects for a bunch of false-positive government that should be academia 
         sector = ifelse(test = str_detect(string = is_gov, pattern = "1"), yes = "government", no = sector),
         sector = ifelse(test = str_detect(string = is_nonprofit, pattern = "1"), yes = "non-profit", no = sector),
         sector = ifelse(test = str_detect(string = is_business, pattern = "1"), yes = "business", no = sector),
         sector = ifelse(test = str_detect(string = new_academic, pattern = "1"), yes = "academic", no = sector),
         sector = ifelse(test = str_detect(string = is_academic, pattern = "1"), yes = "academic", no = sector)) %>% 
  select(login, email, company_original, company, sector, is_academic, is_business, is_gov, is_household, is_nonprofit, is_null) %>% 
  distinct()

classified_users %>% 
  count(sector)

```
```{r}

total_users <- classified_users %>% count()

final_counts <- classified_users %>% 
  group_by(sector) %>% 
  count() %>% 
  arrange(-n) %>% 
  mutate(percentage = round(n / total_users$n, 3),
         perc_wo_missing = round(n / 436534, 3),
         perc_classified = round(n / 174613, 3)) %>% 
  rename(totals = n); final_counts
final_counts$perc_wo_missing[1] <- NA
final_counts$perc_classified[1] <- NA
final_counts$perc_classified[2] <- NA
final_counts

positions <- c("business", "academic","household","government", "non-profit")

sum(final_counts$totals) - 1706873 
sum(final_counts$totals) - 1706873 - 261921

100 - 79.6
100 - 12.2


```

```{r, fig.height = 7, fig.width=12}
positions <- c("business", "academic","household","government", "non-profit")
final_counts <- data.frame(sector = as.factor(c("business", "academic",
                                                 "household","government", "non-profit")),
                           totals = as.numeric(c("115105", "51980", "4093", "2687", "748")),
                           percentages = as.numeric(c("65.9", "29.8", "2.3", "1.5", "0.04")))

ggplot(data=final_counts, aes(x=sector, y=totals)) +
  geom_bar(stat="identity", fill = "#232D4B") +
  scale_x_discrete(limits = positions) +
  geom_text(aes(label = str_c(percentages,'%'), y = totals),
              position = position_dodge(width = 0.9),
              vjust = -0.5, size=5) +
  theme_minimal() +
  theme(plot.title = element_text(size=23, hjust = 0.45),
        plot.subtitle = element_text(size=15, hjust = 0.45),
        axis.text.y = element_text(size = 16),
        axis.text.x = element_text(size = 16),
        axis.title =element_text(size=18),
        axis.title.x=element_blank()) +
  labs(y = "Total GitHub Users within Sector",
       subtitle = "Using GHTorrent Data") +
  ggtitle("GitHub Users Classified by Economic Sector") 
```

```{r, fig.height = 7, fig.width=12}
select_counts <- data.frame(sector = as.factor(c("business", "academic","household","government", "nonprofit")),
                           totals = as.numeric(c("115105", "51980", "4093", "2687", "748")),
                           percentages = as.numeric(c("65.9", "29.8", "2.3", "1.5", "0.04")))

ggplot(data=select_counts, aes(x=sector, y=percentages)) +
  geom_bar(stat="identity", fill = "#232D4B") +
  scale_x_discrete(limits = positions) +
  theme_minimal() +
  theme(plot.title = element_text(size=23, hjust = 0.45),
        plot.subtitle = element_text(size=15, hjust = 0.45),
        axis.text.y = element_text(size = 16),
        axis.text.x = element_text(size = 16),
        axis.title =element_text(size=18),
        axis.title.x=element_blank()) +
  labs(y = "Percentage of GitHub Users within Sector",
       subtitle = "Using GHTorrent Data") +
  ggtitle("GitHub Users Classified by Economic Sector")
```

```{r}
# connect to postgresql to get our data
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# query the users_gh data from github data 
desc_ctrs_summary <- dbGetQuery(conn, "SELECT * FROM gh.desc_ctrs_summary;")

# disconnect from postgresql database 
dbDisconnect(conn)

commits_user_data <- desc_ctrs_summary %>% 
  left_join(classified_users, by = "login") %>% 
  distinct()

commits_user_data <- commits_user_data %>% 
  mutate(sector = replace_na(sector, "null/missing"),
         is_academic = replace_na(is_academic, 0),
         is_business = replace_na(is_business, 0),
         is_gov = replace_na(is_gov, 0),
         is_household = replace_na(is_household, 0),
         is_nonprofit = replace_na(is_nonprofit, 0),
         is_null = replace_na(is_null, 0))

commits_user_data %>% 
  count(sector) %>% 
  arrange(-n)

total_users_commits <- commits_user_data %>% count()
sum(total_users_commits$n) - 2872158 
sum(total_users_commits$n) - 2872158 - 261921
388455 / sum(total_users_commits$n)

final_counts_commit_data <- commits_user_data %>% 
  group_by(sector) %>% 
  count() %>% 
  arrange(-n) %>% 
  mutate(percentage = round(n / total_users_commits$n, 3),
         perc_wo_missing = round(n / 436534, 3),
         perc_classified = round(n / 174613, 3)) %>% 
  rename(totals = n); final_counts
final_counts_commit_data$perc_wo_missing[1] <- NA
final_counts_commit_data$perc_classified[1] <- NA
final_counts_commit_data$perc_classified[2] <- NA
final_counts_commit_data
```
```{r, fig.height = 7, fig.width=12}
new_select_counts <- data.frame(sector = as.factor(c("business", "academic","houshold","government", "nonprofit")),
                           totals = as.numeric(c("114044", "51343", "4037", "2665", "744")),
                           percentages = as.numeric(c("65.3", "29.4", "2.3", "1.5", "0.04")))

ggplot(data=new_select_counts, aes(x=sector, y=totals)) +
  geom_bar(stat="identity", fill = "#232D4B") +
  scale_x_discrete(limits = positions) +
  theme_minimal() +
  theme(plot.title = element_text(size=23, hjust = 0.45),
        plot.subtitle = element_text(size=15, hjust = 0.45),
        axis.text.y = element_text(size = 16),
        axis.text.x = element_text(size = 16),
        axis.title =element_text(size=18),
        axis.title.x=element_blank()) +
  labs(y = "Total GitHub Users within Sector",
       subtitle = "After Combining GHTorrent & GitHub Commit Data") +
  ggtitle("GitHub Users Classified by Economic Sector")
```
```{r, fig.height = 7, fig.width=12}
new_select_counts <- data.frame(sector = as.factor(c("business", "academic","houshold","government", "nonprofit")),
                           totals = as.numeric(c("114044", "51343", "4037", "2665", "744")),
                           percentages = as.numeric(c("65.3", "29.4", "2.3", "1.5", "0.04")))

ggplot(data=new_select_counts, aes(x=sector, y=percentages)) +
  geom_bar(stat="identity", fill = "#232D4B") +
  scale_x_discrete(limits = positions) +
  theme_minimal() +
  theme(plot.title = element_text(size=23, hjust = 0.45),
        plot.subtitle = element_text(size=15, hjust = 0.45),
        axis.text.y = element_text(size = 16),
        axis.text.x = element_text(size = 16),
        axis.title =element_text(size=18),
        axis.title.x=element_blank()) +
  labs(y = "Percentage of GitHub Users within Sector",
       subtitle = "After Combining GHTorrent & GitHub Commit Data") +
  ggtitle("GitHub Users Classified by Economic Sector")
```

```{r}
academic_commit_data <- commits_user_data %>% 
  left_join(academic %>% select(login, institution, country), by = "login") %>% 
  filter(sector == "academic") 

academic_commit_data %>% 
  select(login, email, institution, company_original) %>% 
  filter(is.na(institution))

academic_counts_sorted_top20 <- academic_commit_data %>% 
  drop_na(institution) %>% 
  filter(institution != "misc. student") %>% 
  count(institution) %>% 
  top_n(n, n = 20) %>% 
  arrange(n)
academic_counts_sorted_top20
```
```{r, by_country, fig.height = 9, fig.width=12, warning = FALSE,  echo=FALSE, message=FALSE}

# rename top universities to make labels shorter
top_universities <- academic_counts_sorted_top20 %>%
  add_column(shorter = c("Northeastern University",
                         "Duke University",
                         "Shanghai Jiao Tong Univ.",
                         "Zhejiang University",
                         "University of Pennsylvania",
                         "Tsinghua University",
                         "Georgia Tech",
                         "Harvard University",
                         "Columbia University",
                          "University of Texas",
                         "University of Illinois",
                         "University of Michigan",
                         "New York University",
                         "Cornell University",
                         "Univ. of Southern California",
                         "University of Washington",
                         "Carnegie Mellon University",
                         "Stanford University",
                         "MIT",
                         "UC Berkeley")) %>%
  add_column(country = c("United States",
                         "United States",
                         "China",
                         "China",
                         "United States",
                         "China",
                         "United States",
                         "United States",
                         "United States",
                         "United States",
                         "United States",
                         "United States",
                         "United States",
                         "United States",
                         "United States",
                         "United States",
                         "United States",
                         "United States",
                         "United States",
                         "United States")) %>%
  #inner_join(academic_counts_sorted) %>%
  arrange(n) %>%
  dt_mutate(shorter = factor(shorter, levels = shorter))


ggplot(top_universities, aes(color = country)) +
  geom_point(aes(x = shorter, y = n), size = 4) +
  geom_segment(data = top_universities, mapping = aes(x = shorter, xend = shorter, y = 0, yend = n), size = 1) +
  scale_color_manual(labels = c("China", "United States"), 
                     values = c("#0E879C", "#E57200")) +
  labs(x = "University", y = "Number of Users", color = "Country", title = "Top-20 Universities by Number of Users") +
  #theme_classic() +
  coord_flip() +
  theme_minimal() +
  theme(plot.title = element_text(size=23, hjust = 0.5),
        axis.title =element_text(size=18),
        axis.title.y =element_blank(),
        axis.text.x = element_text(size = 18),
        axis.text.y = element_text(size = 16),
        legend.title=element_text(size=18, hjust = 0.5, face="bold"),
        legend.text=element_text(size=18),
        legend.position = c(.9, .1),
        legend.justification = c("right", "bottom"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6),
        legend.background = element_rect(fill="white",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) 
```

```{r}
academic_counts <- academic_commit_data %>% 
  drop_na(country) %>% 
  filter(institution != "misc. student") %>% 
  count(country) %>% 
  arrange(-n)
academic_counts
```

```{r, countries_users, fig.height = 9, fig.width = 12, warning = FALSE, echo=FALSE}
#country_frequency_institutions <- academic_counts %>% group_by(country) %>% count(wt = n(), sort = TRUE)

country_frequency_users <- academic_counts %>% 
  filter(country != "NA") %>% 
  mutate(country = tolower(country)) %>% 
  dt_mutate(country = str_replace_all(country, "korea, republic of", "south korea")) %>%
  dt_mutate(country = str_replace_all(country, "russian federation", "russia")) %>%
  group_by(country) %>% 
  count(sort = TRUE, wt = n)
country_users_sorted <- country_frequency_users %>%
  arrange(n) %>%
  dt_mutate(country = factor(country, levels = country))

continent <- c("united states" = "north america",
               "china" = "asia",
               "united kingdom" = "europe",
               "canada" = "north america",
               "germany" = "europe",
               "india" = "asia",
               "brazil" = "south america",
               "japan" = "asia",
               "south korea" = "asia",
               "switzerland" = "europe",
               "australia" = "australia",
               
               "netherlands" = "europe",
               "sweden" = "europe",
               "france" = "europe",
               "colombia" = "south america",
               "spain" = "europe",
               "singapore" = "asia",
               "russia" = "europe",
               "taiwan" = "asia",
               "italy" = "europe",
               "hong kong" = "asia") %>% rev()

ggplot(country_users_sorted[(.N-20):.N, ], aes(color = continent)) +
  geom_point(aes(x = country, y = n), size = 4) +
  geom_segment(data = country_users_sorted[(.N-20):.N, ], mapping = aes(x = country, xend = country, y = 0, yend = n), size = 1) +
  #scale_color_manual(values = c("asia" = "#E57200", "australia" = "#375758", "europe" = "#485C99", "north america" = "#12B2CE", "south america" = "#D7E029")) +
  theme_minimal() +
  labs(x = "Country", y = "Number of Users", title = "Top-20 Countries by Users in Academic Sector") +
  theme(plot.title = element_text(size=23, hjust = 0.5),
        axis.title =element_text(size=18),
        axis.title.y =element_blank(),
        axis.text = element_text(size = 18),
        legend.title=element_text(size=18, hjust = 0.5, face="bold"),
        legend.text=element_text(size=18),
        legend.position = c(.9, .1),
        legend.justification = c("right", "bottom"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6),
        legend.background = element_rect(fill="white",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) +
  scale_y_log10(breaks = c(100, 1000, 10000),  labels = c("100", "1000", "10000")) +
  coord_flip() +
  scale_color_manual(labels=c("asia",  "australia", "europe", "north america","south america"),
                     values=c("#232D4B", "#99BDAD",  "#E57200", "#0E879C", "#D9E12B")) 
```

# now that they are all classified, we will add in the country_code information and write this back to the database 

```{r}
# connect to postgresql to get our data
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# query the users_gh data from github data 
country_codes <- dbGetQuery(conn, "SELECT login, cc_multiple, cc_di, cc_viz, location AS raw_location FROM gh.ctrs_extra;")
city_codes <- dbGetQuery(conn, "SELECT raw_login AS login, raw_city FROM gh.sna_ctr_city_codes;")

# disconnect from postgresql database 
dbDisconnect(conn)

geo_info <- country_codes %>% 
  left_join(city_codes, by = "login") %>% 
  rename(city_info = raw_city)

classified_users <- classified_users %>% 
  left_join(geo_info, by = "login") %>% 
  rename(company_cleaned = company) %>% 
  select(login, sector, city_info, cc_multiple, cc_di, cc_viz, raw_location, email, company_original, company_cleaned) %>% 
  distinct()

classified_users %>% 
  count(cc_viz) %>% 
  arrange(-n)

classified_users
```


```{r}
# connect to postgresql to get our data
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

dbWriteTable(conn, name = c(schema = "gh", name = "sna_ctr_sectors"), classified_users, row.names = FALSE)

# disconnect from postgresql database 
dbDisconnect(conn)

# GRANT ALL PRIVILEGES ON TABLE gh.sna_ctr_sectors TO ncses_oss;  
```










```{r}
combined_user_data %>% 
  filter(is_academic == 1) %>% 
  count()

combined_user_data %>% 
  filter(is_gov == 1) %>%
  count()

combined_user_data %>% 
  filter(is_nonprofit == 1) %>%
  count()

combined_user_data %>% 
  filter(is_household == 1) %>%
  count()

combined_user_data %>% 
  filter(is_business == 1) %>%
  count()

final_counts <- data.frame(sector = as.factor(c("business", "academic","houshold","government", "nonprofit")),
                           total = as.numeric(c("115893", "46403", "5455", "3576", "823")))

positions <- c("business", "academic","houshold","government", "nonprofit")
```

```{r, fig.height = 7, fig.width=12}
ggplot(data=final_counts, aes(x=sector, y=total)) +
  geom_bar(stat="identity",  fill = c("#232D4B", "#E57200", "#D9E12B", "#0E879C", "#E6A01D")) +
  scale_x_discrete(limits = positions) +
  theme_minimal() +
  theme(plot.title = element_text(size=23, hjust = 0.45),
        axis.text.y = element_text(size = 16),
        axis.text.x = element_text(size = 16),
        axis.title =element_text(size=18),
        axis.title.x=element_blank()) +
  labs(y = "Total GitHub Users within Sector") +
  ggtitle("Total GitHub Users Classified by Economic Sector")
```

```{r, echo=FALSE, fig.height = 7, fig.width=12}

top20companies <- company_totals %>% 
  filter(total > 399)

company_positions <- data.frame(company = c("microsoft", "google","red hat", "ibm", "facebook",
                                                 "intel", "thoughtworks","alibaba","tencent", "amazon",
                                                 "baidu", "esri","sap","shopify", "mozilla",
                                                 "pivotal", "oracle","salesforce","yandex", "linkedin"), 
                                   countries = as.factor(c("usa","usa","usa","usa","usa",
                                                 "usa","usa","china","china","usa",
                                                 "china", "usa", "germany", "canada", "usa",
                                                 "usa","usa","usa","russia","usa"))) 
top20companies <- top20companies %>% 
  full_join(company_positions, by = "company")

top20companies$company <- fct_relevel(top20companies$company, "microsoft", "google","red hat", "ibm", "facebook",
                                                 "intel", "thoughtworks","alibaba","tencent", "amazon",
                                                 "baidu", "esri","sap","shopify", "mozilla",
                                                 "pivotal", "oracle","salesforce","yandex", "linkedin")
 
ggplot(top20companies) +
  geom_point(aes(x = company, y = total, colour = countries), size = 4) +
  geom_segment( aes(x=company, xend=company, y=0, yend=total)) +
  #ggtitle("Most Prominent Businesses\nDeveloping OSS (By GitHub Users)") +
  coord_flip() +
  theme_minimal() +
  scale_color_manual(labels=c("canada", "china",   "germany", "russia", "usa"),
                     values=c("#ADD8E6", "#232D4B", "#0E879C",  "#D9E12B", "#E57200")) +
  theme(plot.title = element_text(size=23, hjust = 0.5),
        #axis.title.x=element_blank(),
        axis.title =element_text(size=18),
        axis.title.y =element_blank(),
        #axis.text.x = element_text(size = 18),
        axis.text.y = element_text(size = 16),
        axis.text.x = element_text(size = 16),
        legend.title=element_text(size=18, hjust = 0.5, face="bold"),
        legend.text=element_text(size=18),
        legend.position = c(.9, .6),
        legend.justification = c("right", "bottom"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6),
        legend.background = element_rect(fill="white",
                                  size=0.5, linetype="solid", 
                                  colour ="black")) +
  labs(y = "Total GitHub Users", title = "Most Prominent Businesses\nDeveloping OSS (By GitHub Users)") 
```





