---
title: "Academic Edgelist Construction"
output: html_document
---

```{r loading edgelist data, warning=FALSE, echo=FALSE}
rm(list = ls())

# load packages 
for (pkg in c("tidyverse", "igraph", "data.table", "R.utils", "RPostgreSQL", "countrycode",
              "cowplot", "maditr", "lubridate", "igraph")) {library(pkg, character.only = TRUE)}

# connect to postgresql to get data (in rivanna)
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# query the bipartite edgelist data from github data  
ctr_nodelist <- dbGetQuery(conn, "SELECT * FROM gh.sna_ctr_academic")

# query the bipartite edgelist data from github data  
ctr_edgelist <- dbGetQuery(conn, "SELECT * FROM gh.sna_ctr_edgelist_0819")

# disconnect from postgresql
dbDisconnect(conn)

```

```{r}
academic_ctr_nodelist <- ctr_nodelist %>%
  transmute(login = login, institution = company_cleaned)

# join the institutions to ctr_edgelist
academic_ctr_edgelist <- ctr_edgelist %>% 
  # in this file, we do NOT want to filter out self-loops 
  # this would remove all isolates and bias our results for ctr nets 
  #filter(ctr1 != ctr2) %>% 
  rename(login = ctr1) %>% 
  inner_join(academic_ctr_nodelist, by = "login") %>% 
  rename(ctr1 = login, institution1 = institution)

# join the institutions to ctr_edgelist
academic_ctr_edgelist <- academic_ctr_edgelist %>% 
  rename(login = ctr2) %>% 
  inner_join(academic_ctr_nodelist, by = "login") %>% 
  rename(ctr2 = login, institution2 = institution)


#create sna_academic_ctr_edgelist
sna_academic_ctr_edgelist <- academic_ctr_edgelist %>% 
  select(ctr1, ctr2, repo_wts)

sna_academic_institution_edgelist <- academic_ctr_edgelist %>%
  select(institution1, institution2, repo_wts)

```

Let's take a look at the degree distributions to see if the samples compare. 

```{r}
ctr_edgelist %>% 
  count(repo_wts) %>% 
  rename(count = n) %>% 
  filter(repo_wts < 500) %>% 
  ggplot(aes(x=repo_wts, y=count)) +
    geom_bar(stat="identity")

academic_ctr_edgelist %>% 
  count(repo_wts) %>% 
  rename(count = n) %>% 
  filter(repo_wts < 500) %>% 
  ggplot(aes(x=repo_wts, y=count)) +
    geom_bar(stat="identity")

```

Before we write these edgelists to the database, let's make sure that these can be converted to networks in igraph. igraph requires the nodelist and edgelist to match when you draw from both and I find this to be a good test that all the data is aligned. 

```{r}
# we will bring together our new academic_ctr_network & original nodelist (without the institutions split into new rows)
academic_ctr_network <- graph.data.frame(sna_academic_ctr_edgelist, directed = FALSE)

# extract the nodelist from our new network  
sna_academic_ctr_nodelist <- data.frame(id = c(1:(igraph::vcount(academic_ctr_network))), login = igraph::V(academic_ctr_network)$name)

# counting the number of isolates 
gorder(academic_ctr_network) 
gsize(academic_ctr_network)
sum(degree(simplify(academic_ctr_network))==0)
mean(degree(academic_ctr_network))
```

Now that we know the nodelists and edgelists converge to form networks, we can write them to the database.

```{r writing_academic_edgelist, warning=FALSE, echo=FALSE}

# connect to postgresql to get data (in rivanna)
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# write the edgelist to the database
dbWriteTable(conn, name = c(schema = "gh" , name = "sna_academic_ctr_edgelist_0819"), 
             value = sna_academic_ctr_edgelist, row.names = FALSE, temporary = TRUE)
dbWriteTable(conn, name = c(schema = "gh" , name = "sna_academic_institution_edgelist_0819"), 
             value = sna_academic_institution_edgelist, row.names = FALSE, temporary = TRUE)

# disconnect from postgresql
dbDisconnect(conn)

```








