---
title: "International Contributor + Country Edgelist Construction"
output: html_document
---

```{r loading edgelist data, warning=FALSE, echo=FALSE}
rm(list = ls())

# load packages 
for (pkg in c("tidyverse", "igraph", "data.table", "R.utils", "RPostgreSQL", "countrycode",
              "cowplot", "maditr", "lubridate", "igraph")) {library(pkg, character.only = TRUE)}

# connect to postgresql to get data (in rivanna)
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# query the bipartite edgelist data from github data  
ctr_nodelist <- dbGetQuery(conn, "SELECT login, country_code
                                  FROM gh.login_ctry_codes")

# query the bipartite edgelist data from github data  
ctr_edgelist <- dbGetQuery(conn, "SELECT ctr1, ctr2, year, repo_wts 
                                  FROM gh.sna_ctr_edgelist_yxy
                                  WHERE year > 2007 AND year < 2020")

# disconnect from postgresql
dbDisconnect(conn)

```

```{r}

# some ctrs used continents in location data. let's remove that by 
# creating a list and defining a %notin% function to remove them. 
omitted_geographies <- c("europe", "asia", "africa", "americas", "multiple")
`%notin%` <- Negate(`%in%`)

# removes our list of omitted_geographies 
intl_ctr_nodelist <- ctr_nodelist %>% 
  dplyr::mutate(country_code = ifelse(test = str_detect(string = country_code,
                                      pattern = ","), paste("multiple"), no = country_code)) %>% 
  filter(country_code %notin% omitted_geographies)

# join the country_codes to ctr_edgelist
intl_ctr_edgelist <- ctr_edgelist %>% 
  rename(login = ctr1) %>% 
  inner_join(intl_ctr_nodelist, by = "login") %>% 
  rename(ctr1 = login, ctrycode1 = country_code) %>% 
  select(ctr1, ctrycode1, ctr2, repo_wts, year) # this joins cc to original edgelist, gets longer bc of multiple ctry_codes

# join the country_codes to ctr_edgelist
intl_ctr_edgelist <- intl_ctr_edgelist %>% 
  rename(login = ctr2) %>% 
  inner_join(intl_ctr_nodelist, by = "login") %>% 
  rename(ctr2 = login, ctrycode2 = country_code) %>%  
  select(ctr1, ctrycode1, ctr2, ctrycode2, year, repo_wts) 

# changing country codes to country name 
intl_ctr_edgelist$country1 <- countrycode(intl_ctr_edgelist$ctrycode1, 
                                      origin = 'iso2c', 
                                      destination = 'country.name')
intl_ctr_edgelist$country2 <- countrycode(intl_ctr_edgelist$ctrycode2, 
                                      origin = 'iso2c', 
                                      destination = 'country.name')

# changing Kosovo to have a valid country name 
intl_ctr_edgelist <- intl_ctr_edgelist %>% 
  mutate(country1 = ifelse(test = str_detect(string = ctrycode1, 
                          pattern = "xk"), yes = "Kosovo", no = country1)) %>%  
  mutate(country2 = ifelse(test = str_detect(string = ctrycode2, 
                          pattern = "xk"), yes = "Kosovo", no = country2)) %>% 
  select(ctr1, ctrycode1, country1, ctr2, ctrycode2, country2, year, repo_wts)

#create sna_intl_ctr_edgelist
sna_intl_ctr_edgelist <- intl_ctr_edgelist %>% 
  select(ctr1, ctr2, year, repo_wts)

#create sna_intl_ctry_edgelist
sna_intl_ctry_edgelist <- intl_ctr_edgelist %>% 
  select(country1, country2, ctrycode1, ctrycode2, year, repo_wts) %>% 
  group_by(country1, country2, ctrycode1, ctrycode2, year) %>% 
  summarize(repo_wts = sum(repo_wts))

```

Before we write these edgelists to the database, let's make sure that these can be converted to networks in igraph. igraph requires the nodelist and edgelist to match when you draw from both and I find this to be a good test that all the data is aligned. 

```{r}

# we will bring together our new intl_ctr_network & original nodelist (without the country_codes split into new rows)
intl_ctr_network <- graph_from_data_frame(d=sna_intl_ctr_edgelist, vertices=ctr_nodelist, directed=FALSE) 

# from the recoded intl_ctr_nodelist, let's create a nodelist of all distinct country_codes
intl_ctry_nodelist <- intl_ctr_nodelist %>% 
  select(country_code) %>% 
  distinct(country_code, .keep_all = TRUE) %>% 
  arrange(country_code)

# also need to create a test edgelist that just has the country codes 
sna_intl_ctry_edgelist_test <- sna_intl_ctry_edgelist %>% 
  select(country1, country2)

# and then test to see if our network works out 
intl_ctry_network <- graph_from_data_frame(d=sna_intl_ctry_edgelist_test, vertices=intl_ctry_nodelist, directed=FALSE) 

```

Now that we know the nodelists and edgelists converge to form networks, we can write them to the database.

```{r writing_intl_edgelist, warning=FALSE, echo=FALSE}

# connect to postgresql to get data (in rivanna)
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# write the edgelist to the database
dbWriteTable(conn, name = c(schema = "gh" , name = "sna_intl_ctry_edgelist"), 
             value = sna_intl_ctry_edgelist, row.names = FALSE)

# write the edgelist to the database
dbWriteTable(conn, name = c(schema = "gh" , name = "sna_intl_ctr_edgelist"), 
             value = sna_intl_ctr_edgelist, row.names = FALSE)

# disconnect from postgresql
dbDisconnect(conn)

```

# Note that the contributor and country nodelists are in 02_international-collaboration > 01_data-cleaning folder. 









