---
title: "Geographical Analyses of GitHub Users"
description: "This page focuses on mapping GitHub users around the world."
output: 
  rmarkdown::html_document:
    toc: true
    toc_float: true
    highlight: tango
editor_options: 
  chunk_output_type: console
tags: ["R","nlp","regex","big data","interactive map"]
weight: 1
draft: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loading data, message=FALSE, warning=FALSE, include=FALSE}
rm(list = ls())

# load packages
for (pkg in c("tidyverse", "data.table", "R.utils", "RPostgreSQL", "cowplot", "maditr", "stringr", "stringi",  "dplyr", "leaflet", "leaflet.extras")) {library(pkg, character.only = TRUE)}


# connect to postgresql to get our data
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# query the city code data
city_clean_final <- dbGetQuery(conn, "SELECT *
                              FROM gh.sna_ctr_city_codes")


# disconnect from postgresql database 
dbDisconnect(conn)

#https://coolors.co/232d4b-2c4f6b-0e879c-60999a-d1e0bf-d9e12b-e6ce3a-e6a01d-e57200-fdfdfd
uva_color_palette <- 
c("#232D4B", #space cadet
  "#2C4F6B", #indigo dye
  "#0E879C", #blue munsell
  "#60999A", #cadet blue
  "#D1E0BF", #tea green
  "#D9E12B", #pear
  "#E6CE3A", #citrine
  "#E6A01D", #marigold
  "#E57200" #princeton orange
)

CapStr <- function(y) {
  c <- strsplit(y, " ")[[1]]
  paste(toupper(substring(c, 1,1)), substring(c, 2),
        sep="", collapse=" ")
}
```

We conducted analysis on GitHub users' geographic location, which was scraped from their public user profile. In our analysis we are focusing on the GitHub users who has contributed in a licensed R package. While 77.23% geographic information (country and city name) were missing, we were still able to map `r sum(!duplicated(city_clean_final$raw_login))` GitHub users in our final analyses.

### Forming city code
The goal of forming city code is to understand the city-levl network. This will enable us to answer questions like what's the most influential city? Is this city more likely to form domestic collaborations or international collaborations? Our city code is a combination of country name, city name and geocode (latitude and longitude). Geocode is critical to differentiate two city within the same country.You will be surprised to see how many [Greenvilles are there in the U.S.](https://en.wikipedia.org/wiki/Greenville) Meanwhile, the original geocode is accurate to the sixth digit, users located in the same city might have slightly different gocode. We propose a geocode cleaning and aggreating process:    
**Cleaning**: round the geocode (latitude+longitude) to a whole number.    
**Aggregating**: group the cities with geocode that are within 2 degree difference together.   

```{r clean citycode, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
#aggregate by continent
city_clean_final_aggregate_continent<- city_clean_final%>%
  group_by(c_continent_name)%>%
  summarize(ttl_users = n(), `percent (%)` = round(ttl_users/nrow(city_clean_final)*100, digits = 2))%>%
  arrange(desc(ttl_users))

#aggregate by country
city_clean_final_aggregate_country <- city_clean_final%>%
  group_by(c_country_name)%>%
  summarize(ttl_users = n())%>%
  arrange(desc(ttl_users))
#city_clean_final_aggregate_country$country_code <- gsub(" ", "", city_clean_final_aggregate_country$country_code, fixed = TRUE)

#aggregate by U.S. state

#aggregate by city
city_clean_final_aggregate <- city_clean_final%>%
  group_by(c_city_code, c_country_name)%>%
  summarize(ttl_users = n(), lat = mean(raw_lat), long = mean(raw_long))%>%
  arrange(-ttl_users)

city_clean_final_aggregate$city <- str_extract(city_clean_final_aggregate$c_city_code,"_(.*)_") 
city_clean_final_aggregate$city <- gsub("_", "", city_clean_final_aggregate$city, fixed = TRUE)
city_clean_final_aggregate$city<- sapply(city_clean_final_aggregate$city,CapStr)

city_clean_final_aggregate$city_country <- paste(city_clean_final_aggregate$city, city_clean_final_aggregate$c_country_name, sep = ", ")


top_city_vector <- as.vector(city_clean_final_aggregate[1:10,]$c_city_code)

city_clean_final_aggregate <- city_clean_final_aggregate%>%
  mutate(top_city = if_else(c_city_code %in% top_city_vector, "topcity", "not topcity"))
```


### Top Continents Where GitHub Users are Located 

North America is the continent with the highest number of GitHub users - followed by Europe and Asia.

```{r fig.width=9.5, fig.height=6, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gh_continent<- city_clean_final_aggregate_continent%>%
  arrange(desc(ttl_users))

gh_continent$Continent_Name <- factor(gh_continent$c_continent_name, levels = gh_continent$c_continent_name[order(gh_continent$ttl_users)])

min = min(gh_continent$ttl_users)
max = max(gh_continent$ttl_users)

ggplot(gh_continent, aes(x = Continent_Name, y = ttl_users, fill = ttl_users))+
  geom_bar(stat = "identity")+ 
  scale_fill_continuous(low = uva_color_palette[3], high=uva_color_palette[2], breaks=c(min,50000,100000,150000,max), labels = c(as.character(min),"50000","100000","150000", as.character(max)))+
  labs(#title = "Continents where Github users are located", 
       x = "Continent", y = "Total Number of Users", fill = "Total Number \n    of Users") +
  scale_y_continuous(breaks=c(min,50000,100000,150000,max), labels = c(as.character(min),"50000","100000","150000", as.character(max))) +
  theme_bw() +
  theme( legend.spacing.y = unit(1,"cm"))
```

### Top Countries Where GitHub Users are Located 

United States has the highest number of GitHub users with nearly four times as much as China, United Kingdom, or India.

```{r fig.width=9.5, fig.height=6, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gh_country <- city_clean_final_aggregate_country%>%
  arrange(desc(ttl_users))%>%
  top_n(10, ttl_users)

gh_country$c_country_name <- factor(gh_country$c_country_name, levels = gh_country$c_country_name[order(gh_country$ttl_users)])



min = min(gh_country$ttl_users)
max = max(gh_country$ttl_users)

ggplot(gh_country, aes(x = c_country_name, y = ttl_users, fill = ttl_users)) +
  geom_bar(stat = "identity")+ 
  scale_fill_continuous(
    low = "#E6890F", 
    high=uva_color_palette[9], 
    breaks=c(min, 60000, 100000, 140000, max), 
    labels = c(
      as.character(min), 
      "60000",
      "100000",
      "140000",
      as.character(max)
      )
    )+
  labs(#title = "Countries where Github users are located", 
       x = "Country", y = "Total Number of Users", fill = "Total Number \n    of Users") +
  theme_bw()+
  theme(legend.spacing.y = unit(1,"cm"))
```


### Top Cities Where GitHub Users are Located 

San Francisco (US) is the city that has the highest number of GitHub users - followed by London (UK), New York (US), Moscow (Russia), and Beijing (China).

```{r fig.width=11, fig.height=6, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gh_city <- city_clean_final_aggregate%>%
  arrange(-ttl_users)%>%
 # top_n(10, ttl_users)%>%  #don't know why this code doesn't work
  filter(ttl_users >= 6651) 

gh_city$city_country <- str_replace_all(gh_city$city_country, fixed(","), "\n") 


gh_city$city_country <- factor(gh_city$city_country, levels = gh_city$city_country[order(gh_city$ttl_users)])
# NOTE ::: Could you please shorten the labels for the USA and Russia cities 



min = min(gh_city$ttl_users)
max = max(gh_city$ttl_users)

ggplot(gh_city, aes(x = city_country, y = ttl_users, fill = ttl_users))+
  geom_bar(stat = "identity") + 
  scale_fill_continuous(
    low = uva_color_palette[3], 
    high=uva_color_palette[2],
   breaks=c(0,min, 8000, 10000,12000, 14000,max), 
    labels = c("0", as.character(min),"8000", "10000",  "12000", "14000",as.character(max))
   )+
  labs(#title = "Countries where Github users are located", 
       x = "City", y = "Total Number of Users", fill = "Total Number \n    of Users")+
  theme_bw()+
  scale_y_continuous(breaks=c(0,2000, 4000, 6000, 8000, 10000,12000, 14000,max), 
    labels = c("0", "2000", "4000", "6000","8000", "10000",  "12000", "14000",as.character(max)))+
  theme(legend.spacing.y = unit(1,"cm"))
```

### City-Level Interactive Map of GitHub Users

In this map, the size of the circle indicates how many GitHub users reported living or working in each city. You can zoom in and hover over the circle to see how many users are in that city. You can also type in the city that you are interested in the search .

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#In this map, the color of the circle indicates the number of github users in each city, still under development.
city_clean_final_aggregate_top <- city_clean_final_aggregate%>%
  filter(ttl_users > 10)%>%
  mutate(ttl_users_t = log(ttl_users), perc = ttl_users_t/max(ttl_users_t))

pal <- colorFactor(
  palette = c(uva_color_palette[2], uva_color_palette[9]),
  levels = c( "not topcity", "topcity")
)

#ttl user indicated by size
city_clean_final_aggregate%>%
#  mutate(ttl_users_exp = exp(ttl_users)^(1/3))%>%
  leaflet()%>%
  addTiles()%>%
  addSearchOSM()%>%
  addReverseSearchOSM()%>%
  clearMarkers()%>%
  addResetMapButton()%>%
  addCircleMarkers(
    lng = ~long , 
    lat = ~lat, 
    label = ~ paste(city_country,", ", ttl_users, " user(s)", sep = ""),
    radius = ~ttl_users^(1/3), 
    color  = ~pal(top_city))%>% 
  addLegend(pal = pal, values = c( "not topcity", "topcity"))
```

