---
title: "International Contributor + Country Edgelist Construction"
output: html_document
---

```{r loading edgelist data, warning=FALSE, echo=FALSE}
rm(list = ls())

analysis_year <- "0819" 

# load packages 
for (pkg in c("tidyverse", "igraph", "data.table", "R.utils", "RPostgreSQL", "countrycode",
              "cowplot", "maditr", "lubridate", "igraph")) {library(pkg, character.only = TRUE)}

# connect to postgresql to get data (in rivanna)
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# query the bipartite edgelist data from github data  
ctr_nodelist <- dbGetQuery(conn, "SELECT login, country_code_vis
                                  FROM gh_sna.sna_ctr_ctry_codes")
ctr_nodelist <- ctr_nodelist %>% rename(country_code = country_code_vis)
  
# query the bipartite edgelist data from github data  
ctr_edgelist <- dbGetQuery(conn, str_c("SELECT ctr1, ctr2, repo_wts 
                                        FROM gh_sna.sna_ctr_edgelist_dd_lchn_", analysis_year,
                                       " WHERE ctr1 NOT IN (SELECT * FROM gh.bots_table)
                                       AND ctr2 NOT IN (SELECT * FROM gh.bots_table);"))

# disconnect from postgresql
dbDisconnect(conn)

ctr_edgelist # reminder: we WANT loops because they are also isolates
```

```{r}

# some ctrs used continents in location data. let's remove that by 
# creating a list and defining a %notin% function to remove them. 
omitted_geographies <- c("europe", "asia", "africa", "americas", "multiple", "ficticious_places", 
                         "middle_east", "planet_earth", "somewhere_in_space", "worldwide_web")
`%notin%` <- Negate(`%in%`)

# removes our list of omitted_geographies 
intl_ctr_nodelist <- ctr_nodelist %>% 
  drop_na(country_code) %>% 
  dplyr::mutate(country_code = ifelse(test = str_detect(string = country_code,
                                      pattern = ","), paste("multiple"), no = country_code)) %>% 
  filter(country_code %notin% omitted_geographies)

# join the country_codes to ctr_edgelist
intl_ctr_edgelist <- ctr_edgelist %>% 
  # in this file, we do NOT want to filter out self-loops 
  # this would remove all isolates and bias our results for ctr nets 
  #filter(ctr1 != ctr2) %>% 
  rename(login = ctr1) %>% 
  inner_join(intl_ctr_nodelist, by = "login") %>% 
  rename(ctr1 = login, ctrycode1 = country_code) %>% 
  select(ctr1, ctrycode1, ctr2, repo_wts) 
# this joins cc to original edgelist, gets longer bc of multiple ctry_codes

# join the country_codes to ctr_edgelist
intl_ctr_edgelist <- intl_ctr_edgelist %>% 
  rename(login = ctr2) %>% 
  inner_join(intl_ctr_nodelist, by = "login") %>% 
  rename(ctr2 = login, ctrycode2 = country_code) %>%  
  select(ctr1, ctrycode1, ctr2, ctrycode2, repo_wts) 

# changing country codes to country name 
intl_ctr_edgelist$country1 <- countrycode(intl_ctr_edgelist$ctrycode1, 
                                      origin = 'iso2c', 
                                      destination = 'country.name')
intl_ctr_edgelist$country2 <- countrycode(intl_ctr_edgelist$ctrycode2, 
                                      origin = 'iso2c', 
                                      destination = 'country.name')

# changing Kosovo to have a valid country name 
intl_ctr_edgelist <- intl_ctr_edgelist %>% 
  mutate(country1 = ifelse(test = str_detect(string = ctrycode1, 
                          pattern = "xk"), yes = "Kosovo", no = country1)) %>%  
  mutate(country2 = ifelse(test = str_detect(string = ctrycode2, 
                          pattern = "xk"), yes = "Kosovo", no = country2)) %>% 
  select(ctr1, ctrycode1, country1, ctr2, ctrycode2, country2, repo_wts)

#create sna_intl_ctr_edgelist
sna_intl_ctr_edgelist <- intl_ctr_edgelist %>% 
  select(ctr1, ctr2, repo_wts)

#create sna_intl_ctr_edgelist
sna_intl_ctry_edgelist <- intl_ctr_edgelist %>% 
  select(country1, country2, repo_wts)

#intl_ctr_edgelist
#intl_ctr_edgelist %>% filter(is.na(ctrycode1) | is.na(ctrycode1))

#create sna_intl_ctry_edgelist
sna_intl_ctry_edgelist <- intl_ctr_edgelist %>% 
  select(country1, country2, repo_wts) %>% 
  group_by(country1, country2) %>% 
  summarise(repo_wts = sum(repo_wts)) %>% 
  arrange(-repo_wts)

sna_intl_ctry_edgelist
```

Let's take a look at the degree distributions to see if the samples compare. 

```{r}

sna_intl_ctry_edgelist %>% 
  count(repo_wts) %>% 
  rename(count = n) %>% 
  filter(repo_wts < 500) %>% 
  ggplot(aes(x=repo_wts, y=count)) +
    geom_bar(stat="identity")

```

Before we write these edgelists to the database, let's make sure that these can be converted to networks in igraph. igraph requires the nodelist and edgelist to match when you draw from both and I find this to be a good test that all the data is aligned. 

```{r}
# makes network 
intl_ctry_network <- graph.data.frame(sna_intl_ctry_edgelist, directed = FALSE)
# extract the nodelist from our new network  
sna_intl_ctr_nodelist <- data.frame(id = c(1:(igraph::vcount(intl_ctry_network))), 
                                    login = igraph::V(intl_ctry_network)$name)
# counting the number of isolates 
gorder(intl_ctry_network) 
gsize(intl_ctry_network)
sum(degree(simplify(intl_ctry_network))==0)
mean(degree(intl_ctry_network))
#degree(intl_ctr_network)
```

Now that we know the nodelists and edgelists converge to form networks, we can write them to the database.

```{r writing_intl_edgelist, warning=FALSE, echo=FALSE}
# connect to postgresql to get data (in rivanna)
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))
# write the edgelist to the database
dbWriteTable(conn, name = c(schema = "gh_sna", 
                            name = str_c("sna_intl_ctry_edgelist_dd_lchn_nbots_", analysis_year)), 
             value = sna_intl_ctry_edgelist, row.names = FALSE, temporary = TRUE)
# disconnect from postgresql
dbDisconnect(conn)
```

# Note that the contributor and country nodelists are in 02_international-collaboration > 01_data-cleaning folder. 

```{sql}
GRANT ALL PRIVILEGES ON gh_sna.sna_intl_ctry_edgelist_dd_lchn_nbots_08 TO ncses_oss;
GRANT ALL PRIVILEGES ON gh_sna.sna_intl_ctry_edgelist_dd_lchn_nbots_0809 TO ncses_oss;
GRANT ALL PRIVILEGES ON gh_sna.sna_intl_ctry_edgelist_dd_lchn_nbots_0810 TO ncses_oss;
GRANT ALL PRIVILEGES ON gh_sna.sna_intl_ctry_edgelist_dd_lchn_nbots_0811 TO ncses_oss;
GRANT ALL PRIVILEGES ON gh_sna.sna_intl_ctry_edgelist_dd_lchn_nbots_0812 TO ncses_oss;
GRANT ALL PRIVILEGES ON gh_sna.sna_intl_ctry_edgelist_dd_lchn_nbots_0813 TO ncses_oss;
GRANT ALL PRIVILEGES ON gh_sna.sna_intl_ctry_edgelist_dd_lchn_nbots_0814 TO ncses_oss;
GRANT ALL PRIVILEGES ON gh_sna.sna_intl_ctry_edgelist_dd_lchn_nbots_0815 TO ncses_oss;
GRANT ALL PRIVILEGES ON gh_sna.sna_intl_ctry_edgelist_dd_lchn_nbots_0816 TO ncses_oss;
GRANT ALL PRIVILEGES ON gh_sna.sna_intl_ctry_edgelist_dd_lchn_nbots_0817 TO ncses_oss;
GRANT ALL PRIVILEGES ON gh_sna.sna_intl_ctry_edgelist_dd_lchn_nbots_0818 TO ncses_oss;
GRANT ALL PRIVILEGES ON gh_sna.sna_intl_ctry_edgelist_dd_lchn_nbots_0819 TO ncses_oss;
```





