---
title: "01 City Code Formation-And Overview of City-levle Githubu Users"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r loading data, message=FALSE, warning=FALSE, include=FALSE}
rm(list = ls())

# load packages 
for (pkg in c("tidyverse", "data.table", "R.utils", "RPostgreSQL", "cowplot", "maditr", "stringr", "stringi",  "dplyr", "leaflet", "leaflet.extras", "sp", "maps", "maptools", "statebins", "tools", "statebins","sp", "maps", "maptools")) {library(pkg, character.only = TRUE)}


# connect to postgresql to get our data
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# query the users_gh data from github data 
users_gh <- dbGetQuery(conn, "SELECT login, created_at, city, state, country_code, location, long, lat
                              FROM gh.ctrs_raw")

ctrs_extra <- dbGetQuery(conn, "SELECT login, created_at, city, state, country_code, location, long, lat, cc_multiple, cc_viz
                              FROM gh.ctrs_extra")

country_code_dict <- dbGetQuery(conn, "SELECT *
                                FROM datahub.country_codes")
# disconnect from postgresql database 
dbDisconnect(conn)

source("~/git/dspg20oss/src/geographic/00_functions.R", echo = T, prompt.echo = "", spaced = F)
```

# Finished product
## Write the updated citycode to pgAdmin
```{r}
ls_cleancity <- cleancity(ctrs_extra, country_code_dict)

city_clean_final <- ls_cleancity$cleaned_df
table(is.na(city_clean_final$c_city_code)) #limit to ppl who have city code
colnames(city_clean_final)#check the variables

# reconnecting to the database 
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))
# writing the new city_clean_finall table to postgis_2
dbWriteTable(conn, c("gh", "sna_ctr_city_codes"), city_clean_final, row.names=F)
# disconnect from postgresql database  
dbDisconnect(conn)

#grant access on pgAdmin
#GRANT SELECT ON TABLE gh.___ TO ncses_oss;  
```


# Process forming city code
```{r eda, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

user_us <- users_gh%>%
  filter(country_code == "us ")

# 1. github user
# check: users who don't have any of city, state, location, long, lat, don't have country code
# user_geo_na <- users_gh %>%
#   filter(is.na(state))%>%
#   filter(is.na(city))%>%
#   filter(is.na(location))%>%
#   filter(is.na(long), is.na(lat))
# table(is.na(user_geo_na$country_code)) #all users have country code

# filter out users with no country/city
perc_missing <- sum(is.na(users_gh$country_code) | is.na(users_gh$city))/nrow(users_gh) #percent missing
sample_size <- nrow(users_gh)- sum(is.na(users_gh$country_code) | is.na(users_gh$city)) #number of gh users after exlucding missing country code or city

# some users who are missing country code have cities, but cities might not be reliable
users_gh_countrycode_na <- users_gh%>%
  filter(is.na(country_code))

# check: users created year
# class(users_gh$created_at) 
# users_gh_clean <- users_gh_clean %>%
#   mutate(created_year = substring(created_at, 1,4)) #extract year from the date
# table(users_gh_clean$created_year)
```

# Country Level Github Users
```{r country level, echo=FALSE}
# summarize ttl number of users in each country
country_by_ttl_user <- users_gh%>%
  filter(!is.na(country_code))%>%
  group_by(country_code)%>%
  dplyr::summarize(ttl_users = n())%>%
  arrange(desc(ttl_users)) %>%
  top_n(n= 10, wt = ttl_users)

country_by_ttl_user$country_code <- factor(country_by_ttl_user$country_code, levels = country_by_ttl_user$country_code[order(country_by_ttl_user$ttl_users)])

ggplot(country_by_ttl_user, aes(x = country_code, y = ttl_users)) +
  geom_point() +
  labs(title = "Countries where Github users are located", x = "country", y = "total number of users") +
  theme_bw() 
```



# City code formation
We exclude users who did not provide either country code or city information. (`r perc_missing`% missing), which leaves us `r sample_size` samples in the dataset. Note that country code is extracted from country, city, loaction, and longitude and latitude. Country code is missing if the user did not provide any of these information. Since we are interested in users at the city level, if we are missing city information, we could not extract a unique city.    

We formed city code in the following steps:   

First, we want to differentiate cities from different countries. We form a new variable "city_code", which is a concactinated form of country code and city. Since there could be multiples cities with the same name in different countries, "city_code" can be used to differentiate cities from from different countries.

Next, we want to differentiate cities within a country. Although we have state variable, but we decide no to use this variable due to the inaccurate report. We decide to use longitude and latitude to differentiate cities in different areas in a country. However, longtitude and latitude could vary from a small digit even though they indicate one city. We decide to group cities together if their long & lat deviate within a sum of 2 degrees. 

The final "city_code" is a concactinated form of:
  -country code (generated)
  -city
  -latitude (round to a whole number)
  -longitude (round to a whole number)

# city code analysis
```{r city code and visualization, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
### analysis
cleancitycode_analysis <- ls_cleancity$analysis_df

city_non_benchmark <- cleancitycode_analysis%>%
  filter(benchmark == F)
#each dot represents a geographic location that has multiple longitude and latitude
ggplot(city_non_benchmark, aes(x = diff_sum, y = ttl_users)) +
  geom_point(size = 0.5)  + 
  aes(colour = combine) + 
  theme(legend.position = "right") + 
  labs(title = "")

#distribution of the sum of differences in longitude and latitude at each of the geographic location comparing to the benchmarked city.
ggplot(city_non_benchmark, aes(x = diff_sum)) +
  geom_histogram(binwidth = 3.9) + 
  labs(title="Distribution of the distance between each geographic location with the benchark city",
        x ="sum of difference in longitude and latitude")+
  theme(plot.title = element_text(size=9))

# 20% of 
table(city_non_benchmark$combine)
```


# Examine city code quality by comparing with user input
```{r}
us_greenville <- city_clean_final%>%
  filter(country_code == "us ")%>%
  filter(city == "greenville")%>%
  group_by(city_code, state,location)%>%
  summarize(N=n())


us_sanfrancisco<- city_clean_final%>%
  filter(country_code == "us ")%>%
  filter(city == "san francisco")%>%
  group_by(state,  long, lat)%>%
  summarize( N=n())


us_sanfrancisco_location<- city_clean_final%>%
  filter(country_code == "us ")%>%
  filter(city == "san francisco")%>%
  group_by(state, long, lat,  location)%>%
  summarize( N=n())
```
