---
title: "07 Form City Edgelist"
output: html_document
---

```{r loading edgelist data, warning=FALSE, echo=FALSE}
rm(list = ls())

# load packages 
for (pkg in c("tidyverse", "igraph", "data.table", "R.utils", "RPostgreSQL", "countrycode",
              "cowplot", "maditr", "lubridate", "igraph")) {library(pkg, character.only = TRUE)}

# connect to postgresql to get data (in rivanna)
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# query the bipartite edgelist data from github data  
ctr_nodelist_all <- dbGetQuery(conn, "SELECT * FROM gh.sna_ctr_city_codes")

# query the bipartite edgelist data from github data  
#ctr_edgelist <- dbGetQuery(conn, "SELECT * FROM gh.sna_ctr_edgelist_08")
ctr_edgelist <- dbGetQuery(conn, "SELECT * FROM gh.sna_ctr_edgelist_0819")

# disconnect from postgresql
dbDisconnect(conn)

```

```{r}
# some ctrs used continents in location data. let's remove that by 
# creating a list and defining a %notin% function to remove them. 
unique(ctr_nodelist_all$c_continent_name)

# north america network
ctr_nodelist <- ctr_nodelist_all%>%
  filter(c_continent_name == "Oceania")

#contributor 1
city_edgelist <- ctr_edgelist %>% 
  # in this file, we do NOT want to filter out self-loops 
  # this would remove all isolates and bias our results for ctr nets 
  filter(ctr1 != ctr2) %>% 
  rename(login = ctr1) %>% 
  inner_join(ctr_nodelist, by = c( "login" = "raw_login")) %>% 
  rename(ctr1 = login, citycode1 = c_city_code) %>% 
  select(ctr1, citycode1, ctr2, repo_wts)%>%
#contributor 2
  rename(login = ctr2) %>% 
  inner_join(ctr_nodelist, by = c( "login" = "raw_login")) %>% 
  rename(ctr2 = login, citycode2 = c_city_code) %>%  
  select(ctr1, citycode1, ctr2, citycode2, repo_wts) 

#create sna_intl_city_edgelist
city_edgelist <- city_edgelist %>%
  group_by(citycode1, citycode2)%>%
  summarize(ttl_repo = sum(repo_wts))%>%
  rename(from=citycode1, to=citycode2, weight=ttl_repo)%>% 
  rename(source = from, target = to)
```


Before we write these edgelists to the database, let's make sure that these can be converted to networks in igraph. igraph requires the nodelist and edgelist to match when you draw from both and I find this to be a good test that all the data is aligned. 

```{r}

# we will bring together our new intl_ctr_network & original nodelist (without the country_codes split into new rows)
intl_city_network <- simplify(graph.data.frame(city_edgelist, directed = F),
                              remove.loops = FALSE,
                              edge.attr.comb = igraph_opt("edge.attr.comb"))

# extract the nodelist from our new network  
sna_intl_city_nodelist <- data.frame(id = c(1:(igraph::vcount(intl_city_network))), login = igraph::V(intl_city_network)$name)

# counting the number of isolates 
gorder(intl_city_network) 
gsize(intl_city_network)
sum(degree(simplify(intl_city_network))==0)
mean(degree(intl_city_network))
#degree(intl_ctr_network)

```

Now that we know the nodelists and edgelists converge to form networks, we can write them to the database.

```{r writing_intl_edgelist, warning=FALSE, echo=FALSE}

# connect to postgresql to get data (in rivanna)
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# write the edgelist to the database
dbWriteTable(conn, name = c(schema = "gh" , name = "sna_city_oceania_edgelist_0819"), 
             value = city_edgelist, row.names = FALSE, temporary = TRUE)

# disconnect from postgresql
dbDisconnect(conn)


rm(city_edgelist, intl_city_network, sna_intl_city_nodelist, ctr_nodelist, city_nodelist)
```

# Note that the contributor and country nodelists are in 02_international-collaboration > 01_data-cleaning folder. 






