---
title: "Company Counts on GitHub"
author: "Brandon L. Kramer"
date: "11/26/2019"
output: html_document
---

```{r loading data}
rm(list = ls())

# load packages 
for (pkg in c("tidyverse", "igraph", "visNetwork", "data.table", "R.utils", "RPostgreSQL", "cowplot", "maditr", "stringr", "stringi")) {library(pkg, character.only = TRUE)}

# connect to postgresql to get our data
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# query the users_gh data from github data 
users_gh <- dbGetQuery(conn, "SELECT * 
                              FROM gh.ctrs_extra")

# disconnect from postgresql database 
dbDisconnect(conn)
```

```{r}

users_gh

length(users_gh$company) 
# 2,143,407 total entries 
# note: there are actually 2,435,698 total users

valid_company_codes <- users_gh %>% drop_na(company) 
length(valid_company_codes$company)
# 422517 users with some company_code information 
length(valid_company_codes$company) / length(users_gh$company)
# putting us at 19.7124% that are identifiable for now 

users_gh %>% 
  drop_na(company) %>% 
  mutate(organization = str_to_lower(company)) %>% 
  mutate(organization = str_trim(organization)) %>% 
  group_by(organization) %>% 
  count() %>% arrange(-n)

```

```{r company counts}
organization_counts <- users_gh %>% 
  drop_na(company) %>% 
  mutate(organization = str_to_lower(company)) %>% 
  mutate(organization = str_trim(organization)) %>% 
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(freelancer|freelance|freelancing|freelancers|freelances|self|personal|home|private|individual|myself|me|independent|independent contractor|contractor|private|household|house|home|my house|jobless|looking for a job|looking for job|seeking employment|seeking|actively seeking employment|seeking opportunities|seeking internship|seeking work)\\b"), 
                              yes = "household", no = organization)) %>%
  mutate(organization = ifelse(test = str_detect(string = organization, 
                              pattern = "\\b(?i)(n/a|none|null|no|na)\\b"),      
                              yes = "none/null", no = organization)) %>% 
  group_by(organization) %>% count() %>% arrange(-n) 

organization_counts 

```

```{r editing refusal data}

# getting the totals before refusals 
sum(organization_counts$n)
sum(organization_counts$n) / 2435698

# getting the totals of refusals (none/null) 
organization_counts %>% 
  filter(organization == "none/null"|organization == ""|organization == "-") 
39803+3851+311 # total of all three 

# removing country codes in org code column 
organization_counts %>%
  filter(organization == "china"|organization == "japan")
334+183

```

```{r creating final totals }
# removing refusals and countries from dataset 
organization_counts <- organization_counts %>% 
  filter(organization != "none/null") %>% filter(organization != "") %>% filter(organization != "-") %>% 
  filter(organization != "china") %>% filter(organization != "japan")
  
# i used this snippet of code to search through all of the top-50 academic and top-50 non-academic organizations to catch variations 
# filter(organization_counts, grepl('google', organization))

# this gets the total number and percentage of logins with organization codes 
sum(organization_counts$n)
sum(organization_counts$n) / 2435698

# output to a csv file 
write.csv(organization_counts, "organization_counts.csv")
#saveRDS(company_counts, "company_counts.rds")
```

This suggests that only 15% of the data has valid information in the company column. 

```{r}
users_gh %>% filter(is.na(company))
```

When we look at the logins with missing company data, we can find out more about them on their GitHub profiles. A quick check of these top login sites shows that there is additional information out there in their profiles that we could use to identify sector information. For now, let's just try to categorize what we have. 

# Codifying the Data into Sectors 

The original sectors from the GitHub project in Summer 2019 are business, nonprofit, government, university and individual/private. Let's see if we can get some estimates. 

```{r}

# individual, freelancer or student
individual_counts <- organization_counts %>% 
  filter(grepl('(individual|freelancer|student)', organization))
individual_counts
sum(individual_counts$n)
sum(individual_counts$n) / 2435698
# 8365 or 0.34% 

```

```{r}

# government institutions 
government_counts <- organization_counts %>% 
  filter(grepl('(national laboratory|national institute|national institutes|nih|gov|government|authority|council|department|commission|office|county|administration|.gov$)', organization)) %>% 
  filter(!grepl('(college|university)', organization))
government_counts
sum(government_counts$n)
sum(government_counts$n) / 2435698
# 1409 or 0.05% 

```

```{r}

# nonprofit institutions 
nonprofit_counts <- organization_counts %>% 
  filter(grepl('(?i)association|foundation|fund|board of realtors|assoc.|society|societies|organization|.org$', organization)) %>% 
  filter(!grepl('(geckoboard|moduscreateorg)', organization))
nonprofit_counts
sum(nonprofit_counts$n)
sum(nonprofit_counts$n) / 2435698
# 1830 or 0.07%

```

```{r}

# academic institutions 
academic_counts <- organization_counts %>% 
  filter(grepl('(university|college|institute)', organization))
academic_counts
sum(academic_counts$n)
sum(academic_counts$n) / 2435698
# 30789 or 1.26%

```
```{r}

# businesses 
business_counts <- organization_counts %>% 
  filter(grepl('(?i)(corp|.?com|llp|inc.j|corporation)\\.?$|(lc.|Group|Entertainment|Computing|Software)$|Service.*|Consulting|Consultants|Business|Laboratories|Technologies|Technology|Bank|Company|Studios|Solutions|inc.|l\\.?l\\.?c.?|ltd|employer|Systems|System|Limited|Publishing', organization)) %>% 
  filter(!grepl('(?i)(college|university|institute of technology)', organization))
business_counts
sum(business_counts$n)
sum(business_counts$n) / 2435698
# 

```

```{r}

# non-academic institutions 
other_counts <- organization_counts %>% 
  filter(!grepl('(individual|freelancer|student)', organization)) %>% 
  filter(!grepl('(national laboratory|national institute|national institutes|nih|gov|government|authority|council|department|commission|office|county|administration|.gov$)', organization)) %>% 
  filter(!grepl('(?i)association|foundation|fund|board of realtors|assoc.|society|societies|organization|.org$', organization)) %>%
  filter(!grepl('(university|college|institute)', organization)) %>% 
  filter(!grepl('(?i)(corp|.?com|llp|inc.j|corporation)\\.?$|(lc.|Group|Entertainment|Computing|Software)$|Service.*|Consulting|Consultants|Business|Laboratories|Technologies|Technology|Bank|Company|Studios|Solutions|inc.|l\\.?l\\.?c.?|ltd|employer|Systems|System|Limited|Publishing', organization))
other_counts

# write csvs 
#write.csv(non_academic_counts, "non_academic_counts.csv")
#write.csv(academic_counts, "academic_counts.csv")

```








