---
title: "email-cleaning"
author: "Morgan Klutzke"
date: "6/23/2020"
output: html_document
---

```{r packages}
rm(list = ls())

# load packages 
for (pkg in c("tidyverse", "igraph", "visNetwork", "data.table", "R.utils", "RPostgreSQL", "cowplot", "maditr", "stringr", "stringi")) {library(pkg, character.only = TRUE)}
```

```{r loading data}
# connect to postgresql to get our data
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# query the users_gh data from github data 
users_gh <- dbGetQuery(conn, "SELECT login, email, company
                              FROM gh.ctrs_extra")

institutions_hipolabs <- dbGetQuery(conn, "SELECT institution, domains FROM hipolabs.universities")
```

```{r}
# disconnect from postgresql database 
dbDisconnect(conn)
```

Boosting university counts by looking at email domains

```{r}
# Getting just the domains for GitHub users' emails
email_domains <- users_gh %>% drop_na(email) %>%
dt_mutate(domains = str_replace_all(email, "^[a-zA-Z0-9_.+-]+@", ""))

#domain_count <- email_domains %>% group_by(domains) %>% count() %>% arrange(-n)
#domain_count
```

Matching the institutions from hipolabs to GitHub users based on email domains.

We can match the academic institution for 17,514 users based on email domains. But, some of this is redundant or not consistent with what the user already reported for "company". Here we impute the institution only when nothing was entered for company.

```{r}
inferred_institutions <- email_domains %>%
  as.data.table() %>%
  inner_join(institutions_hipolabs) %>%
  subset(is.na(company)) %>%
  dt_mutate(company = institution)

nrow(inferred_institutions)
# 11,688 imputed companies
```

