---
title: "International Collaboration Netwoks: Fitting Power Laws"
output: html_document
---

```{r loading edgelist data}
rm(list = ls())
# install.packages(c("tidyverse", "igraph", "visNetwork", "bc3net", 
# "data.table", "R.utils", "RPostgreSQL", "cowplot", "maditr", "linkprediction", "poweRlaw"))

# load packages 
for (pkg in c("tidyverse", "igraph", "visNetwork", "bc3net", "data.table", "R.utils", "RPostgreSQL",
              "cowplot", "maditr", "lubridate", "linkprediction", "poweRlaw")) {library(pkg, character.only = TRUE)}
```


```{r global_networks_yxy power law fitting}
rm(list = ls())
setwd("~/oss_networks_cum/2008")
g <- read_rds("login_network.rds") 

data <- degree(g)
data <- data[data>0]
data.dist <- data.frame(k=0:max(data),p_k=degree_distribution(g))
data.dist <- data.dist[data.dist$p_k>0,]
ggplot(data.dist) + geom_point(aes(x=k, y=p_k)) + theme_bw()
```

```{r}
m_pl <- displ$new(data)
est_pl <- estimate_xmin(m_pl)
est_pl$xmin # initial estimation of kmin 
est_pl$pars # initial estimation of γ
est_pl$gof # calculate D with Kolgomorov-Smirnov test
```

```{r}
# finish remainder of process using https://rpubs.com/lgadar/power-law
data.s <- unique(data)
d_est <- data.frame(K_min=sort(data.s)[1:(length(data.s)-2)], gamma=rep(0,length(data.s)-2), D=rep(0,length(data.s)-2))
for (i in d_est$K_min){
  d_est[which(d_est$K_min == i),2] <- estimate_xmin(m_pl, xmins = i)$pars
  d_est[which(d_est$K_min == i),3] <- estimate_xmin(m_pl, xmins = i)$gof
}
K.min_D.min <- d_est[which.min(d_est$D), 1]
ggplot(data=d_est, aes(x=K_min, y=D)) + geom_line() + theme_bw() + 
  geom_vline(xintercept=K.min_D.min, colour="red") + annotate("text", x=K.min_D.min, y=max(d_est$D)/3*2, label=K.min_D.min)

```
```{r}
ggplot(data=d_est, aes(x=K_min, y=gamma)) + geom_line() + theme_bw() + 
  geom_vline(xintercept=K.min_D.min, colour="red") + annotate("text", x=K.min_D.min, y=max(d_est$gamma)/3*2, label=K.min_D.min)
```
```{r}
m_pl$setXmin(est_pl)
plot.data <- plot(m_pl, draw = F)
fit.data <- lines(m_pl, draw = F)
ggplot(plot.data) + geom_point(aes(x=log(x), y=log(y))) + labs(x="log(k)", y="log(CDF)") + theme_bw() + 
  geom_line(data=fit.data, aes(x=log(x), y=log(y)), colour="red")
```
```{r}
bs_pl <- bootstrap_p(m_pl, no_of_sims=1000, threads=8, seed = 123)
#threads=core number of processor that used by function
#parallel::detectCores() determines how many cores in your computer
plot(bs_pl)
```

```{r}
df_bs_pl <- bs_pl$bootstraps
ggplot(data=df_bs_pl, aes(pars)) + geom_histogram() + labs(x="gamma", y="frequency") + theme_bw()
```
```{r}
ggplot(data=df_bs_pl, aes(xmin)) + geom_histogram() + labs(x="K_min", y="frequency") + theme_bw()
```
```{r}
gamma_D.min <- d_est[which.min(d_est$D), 2]

ggplot(data=df_bs_pl, aes(x=xmin, y=pars)) + labs(x="K_min", y="gamma") + theme_bw() + 
  geom_point(shape=21, colour="black", fill="red", size=0.5, stroke=2, 
             position = position_jitter(), alpha=0.6) +
  geom_vline(xintercept=K.min_D.min, colour="blue") +
  geom_hline(yintercept=gamma_D.min, colour="blue") +
  annotate("text", x=K.min_D.min, y=min(df_bs_pl$pars), label=K.min_D.min, col="blue") +
  annotate("text", x=min(df_bs_pl$xmin), y=gamma_D.min, label=round(gamma_D.min, digits=2), col="blue")
```
```{r}
D.min <- d_est[which.min(d_est$D), 3]
ggplot(data=df_bs_pl, aes(gof)) + geom_histogram() + labs(x="D", y="frequency") + geom_vline(xintercept=D.min, colour="red") + theme_bw()
```
```{r}
bs_pl$p #p value
```

##################################################### 
#####################################################
##################################################### NOT DONE YET 
#####################################################
#####################################################

## Calculating Power Laws Based on Degree Distribution of Networks (Not Done)

```{r fitting power laws}
power_law_start <- data.frame(event="power_law_start", time=now("EST"))
time_log <- rbind(time_log, power_law_start); rm(power_law_start)

data <- nodelist$degree
data.dist <- data.frame(k=0:max(data),p_k=degree_distribution(login_network))
data.dist <- data.dist[data.dist$p_k>0,]
ggplot(data.dist) + geom_point(aes(x=k, y=p_k)) + theme_bw()

m_pl <- displ$new(data)
est_pl <- estimate_xmin(m_pl)
est_pl$xmin # initial estimation of kmin 
est_pl$pars # initial estimation of γ
est_pl$gof # calculate D with Kolgomorov-Smirnov test

# finish remainder of process using https://rpubs.com/lgadar/power-law

power_law_end <- data.frame(event="power_law_end", time=now("EST"))
time_log <- rbind(time_log, power_law_end); rm(power_law_end)
```

## Normalizing Degree Distribributions with Cosine Similarity Scores (Not Done Yet)

```{r normalizing networks}
cos_norm <- proxfun(login_network, method="cos", value="edgelist") %>% 
  filter(from < to) %>% 
  rename(cos_norm = value)
```

## Testing for Assortativity and Homophily (Not Done Yet)

```{r testing patterns in assortativity and homophily}
# connect to postgresql to get data (in rivanna)
conn <- dbConnect(drv = PostgreSQL(), dbname = "sdad_data", 
                  host = "sdad.policy-analytics.net", port = 5436, 
                  user = Sys.getenv("db_userid"), password = Sys.getenv("db_pwd"))

# query the bipartite edgelist data from github data  
node_attributes <- dbGetQuery(conn, "SELECT name, country_code_vis
                                 FROM github.intl_st_bp_nodes")
# disconnect from postgresql
dbDisconnect(conn); rm(conn)

# adding country codes to the nodelist 
nodelist <- dplyr::full_join(nodelist, node_attributes, by = c("nName" = "login")) %>% 
  dplyr::mutate(new_col = ifelse(test = is.na(x = country_code), yes = paste("repo"), no = country_code)) %>% 
  dplyr::select(-country_code) %>% 
  dplyr::rename(name = nName, country_code = new_col)

# testing homophily based on country_code
assortativity_nominal(net, V(net)$media.type, directed=F)

# using linkprediction to test for structural homophily 



```

## References 

Blondel, V. D., Guillaume, J. L., Lambiotte, R., & Lefebvre, E. (2008). Fast unfolding of communities in large networks. Journal of statistical mechanics: theory and experiment, 2008(10), P10008.

http://pablobarbera.com/big-data-upf/html/02b-networks-descriptive-analysis.html
https://igraph.org/r/doc/cluster_louvain.html
https://kateto.net/networks-r-igraph 
https://sites.fas.harvard.edu/~airoldi/pub/books/BookDraft-CsardiNepuszAiroldi2016.pdf
https://rpubs.com/lgadar/power-law 
http://recon.icm.edu.pl/wp-content/uploads/2019/05/linkprediction.pdf





