---
title: "Static Network Analyses"
author: "Brandon L. Kramer"
date: "10/23/2019"
output: html_document
---

```{r loading edgelist data}
rm(list = ls())
# install.packages(c("tidyverse", "igraph", "visNetwork", "bc3net", "data.table", "R.utils", "RPostgreSQL", "cowplot", "maditr"))

# load packages 
for (pkg in c("tidyverse", "igraph", "visNetwork", "bc3net", "data.table", "R.utils", "RPostgreSQL", "cowplot", "maditr")) {library(pkg, character.only = TRUE)}

# connect to postgresql to get our data
conn <- dbConnect(drv = PostgreSQL(),
                 dbname = "sdad_data",
                 host = "postgis_2",
                 port = 5432L,
                 user = Sys.getenv("db_userid"),
                 password = Sys.getenv("db_pwd"))

# query the static edgelist data from github data 
static_edgelist <- dbGetQuery(conn, "SELECT login, slug, count FROM github.st_bp_edgelist_osi")

# query the static edgelist data from github data 
node_attributes <- dbGetQuery(conn, "SELECT login, country_code FROM github.users_gh_cc")

# disconnect from postgresql
dbDisconnect(conn)
```

Let's make a network and add the country codes and degree centrality totals to the nodelist. 

```{r}
# renaming columms for igraph 
static_edgelist <- static_edgelist %>% dplyr::rename(weight = count)

# this creates a graph and removes duplicated edges and self-loops 
g <- igraph::simplify(igraph::graph.data.frame(static_edgelist, directed=TRUE))

# after creating that network, we need to construct a nodelist 
static_nodelist <- data.frame(ID = c(1:(igraph::vcount(g))), nName = igraph::V(g)$name)

# adding country codes to the nodelist 
static_nodelist <- dplyr::full_join(static_nodelist, node_attributes, by = c("nName" = "login")) %>% 
  dplyr::mutate(new_col = ifelse(test = is.na(x = country_code), yes = paste("repo"), no = country_code)) %>% 
  dplyr::select(-country_code) %>% 
  dplyr::rename(name = nName, country_code = new_col) 

# renaming multiple countries 
static_nodelist <- static_nodelist %>% 
  dplyr::mutate(country_code_vis = ifelse(test = str_detect(string = static_nodelist$country_code,
                                      pattern = "_"), paste("multiple"), no = country_code)) %>% 
  dplyr::mutate(country_code_di = ifelse(test = str_detect(string = static_nodelist$country_code,
                                      pattern = "_"), paste("multiple"), no = "single")) %>% 
  dplyr::select(ID, name, country_code_di, country_code, country_code_vis)

# trimming white space (just in case)
static_nodelist$country_code <- stringi::stri_trim_both(static_nodelist$country_code)
static_nodelist$country_code_di <- stringi::stri_trim_both(static_nodelist$country_code_di)
static_nodelist$country_code_vis <- stringi::stri_trim_both(static_nodelist$country_code_vis)

# getting a count of countries and repos 
static_nodelist %>% 
  dplyr::count(country_code, sort = TRUE) 

# calculating degree centrality 
static_nodelist <- cbind(static_nodelist, nodeDegree=igraph::degree(g, v = igraph::V(g), mode = "all"))

static_nodelist %>% 
  dplyr::arrange(-nodeDegree)
```

Let's write the nodelist and edgelist back to the database to pull that later. 

```{r writing edgelists to sql}
# reconnecting to the database 
conn <- dbConnect(drv = PostgreSQL(),
                 dbname = "sdad_data",
                 host = "postgis_2",
                 port = 5432L,
                 user = Sys.getenv("db_userid"),
                 password = Sys.getenv("db_pwd"))

# writing the new users_gh_cc table to postgis_2
dbWriteTable(conn, c("github", "intl_st_bp_nodes"), static_nodelist)
dbWriteTable(conn, c("github", "intl_st_bp_edges"), static_edgelist)

# disconnect from postgresql database  
dbDisconnect(conn)
```

The next logical step is to run betweenness centrality and community detection, but both are so computationally intensive that we haven't actually gotten them to run yet. As of 10/24/19, we are testing these in Rivanna. 

```{r betweenness and community detection}

# ALL OF THIS MUST BE RUN ON RIVANNA BECAUSE REGULAR (TESTING NOW)

# calculating betweenness centrality 
static_nodelist <- cbind(static_nodelist, nodeBetweenness=igraph::betweenness(g, v = igraph::V(g), directed=TRUE))

betAll <- igraph::betweenness(g, v = igraph::V(g), directed = FALSE) / (((igraph::vcount(g) - 1) * (igraph::vcount(g)-2)) / 2)
betAll.norm <- (betAll - min(betAll))/(max(betAll) - min(betAll))
static_nodelist <- cbind(static_nodelist, nodeBetweenness=betAll.norm) 
rm(betAll, betAll.norm)

# calculating group membership using cluster_walktrap in igraph  
wc <- cluster_walktrap(g)
members <- membership(wc)                                                    # this kills the session 
clusters <- igraph_to_networkD3(g, group = members)
static_nodelist <- cbind(static_nodelist, cluster=clusters$nodes$group)



```


3 columns for cc 
str_split collapse 


rds file = how big is it? 
saveRDS()
small update.

























