---
title: "02 Email Domain Search"
author: "Crystal"
output: 
  rmarkdown::html_document:
    toc: true
    toc_float: true
    highlight: tango
    theme: journal
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Objective
Identify github users' email domains, general and also institutional email domains. Identify patterns. 

# Data
I'm using ctrs_extra table from the gh schema.

```{r loading data, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
rm(list = ls())

# load packages 
for (pkg in c("tidyverse", "data.table", "R.utils", "RPostgreSQL", "cowplot", "maditr", "stringr", "stringi", "mosaic",  "raster", "dplyr",  "ggplot2", "shiny", "plotly", "gt", "glue", "prettydoc")) {
  library(pkg, character.only = TRUE)
}


# connect to postgresql to get our data
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

gh_extra <- dbGetQuery(conn, "SELECT *
                              FROM gh.ctrs_extra")

# disconnect from postgresql database 
dbDisconnect(conn)
```


# Regex for identify email domain
In gh_extra table, we have `r table(is.na(gh_extra$email))[2]/nrow(gh_extra) *100`% (N=`r table(is.na(gh_extra$email))[2]`) missing in email, which leaves us `r table(is.na(gh_extra$email))[1]` github users.

```{r message=FALSE, warning=FALSE}
data_profiling <- function(df){
  variable_type <- apply(df, 2, function(x) class(x))
  num_unique <- apply(df, 2,  function (x) length(unique(x)))
  num_missing <- apply(df, 2, function(x) sum(is.na(x)))
  perc_missing <- apply(df, 2, function(x) round((sum(is.na(x)))/length(x)* 100, digits = 2))  
  summary_table <- as.data.frame(cbind(variable_type, num_unique, num_missing, perc_missing))
  return(summary_table)
}

email_clean <- gh_extra%>%
  filter(!is.na(email))%>%
  select(login, email, country_code)%>%
  #mutate(email_domain_short = str_extract(email, "@[a-z]+"))%>% #the first string after @
  mutate(email_domain_long =  str_extract(email, "(?<=@).*"))%>% #all strings after @
  mutate(edu_email_domain = if_else(str_detect(email, ".edu$") == T, T, F))%>% #end with edu
  mutate(institution = str_extract(email, "(?<=@)(.*)edu")) 
```


# General email domain
```{r message=FALSE, warning=FALSE, paged.print=FALSE}
email_clean %>%
  filter(!is.na(email_domain_long))%>%
  group_by(email_domain_long)%>%
  summarize(N = n(), `percent(%)` = round(N/nrow(email_clean) * 100, digits = 2))%>%
  arrange(desc(N))%>%
  top_n(20, N)%>%
  gt()%>%
   tab_header(
    title = "Top Github User Email Domains"
  )


domain10 <- email_clean %>%
  group_by(email_domain_long)%>%
  summarize(N = n())%>%
  arrange(desc(N))%>%
  filter(!is.na(email_domain_long))%>%
  top_n(20, N)
domain10 <-  as.vector(domain10$email_domain_long)

email_clean %>%
 filter(email_domain_long %in% domain10)%>%
  filter(!is.na(country_code))%>%
  group_by(email_domain_long, country_code)%>%
  summarize(N=n(), `percent(%)` = round(N/nrow(email_clean) * 100, digits = 3))%>%
  arrange(desc(N))%>%
  filter(N > 10)%>%
  top_n(20, N)%>%
  gt()%>%
   tab_header(
    title = "Top Github User Email Domains by Country (>10)"
  )
```


# Institutional emails
```{r}
email_clean %>%
  filter(edu_email_domain == T)%>%
  select(login, email, institution)%>%
  group_by(institution)%>%
  summarize(N = n(), `percent(%)` = round(N/nrow(email_clean) * 100, digits = 2))%>%
  arrange(desc(N))%>%
  top_n(100,N)%>%
  gt()%>%
   tab_header(
    title = "Top Github User Institutional Email Domains"
  )

```

