---
title: "04 Hypothesis Test for Sample Bias"
output: 
  rmarkdown::html_document:
    toc: true
    toc_float: true
    highlight: tango
    theme: journal
editor_options: 
  chunk_output_type: console
---

# Objective
In the geographic analysis, we rely on the geographic location github users provide, which we were able to clean it into country and city. 77.24% gihub users are missing geographic locations. We want to ensure our sample is not bias, that is representitive to the github users that we are interested in. Here we conduct hypothesis test to see whether the github users who have geographic location differ from the users who do not have geographic location, in the sense of contribution to open source softwares.

```{r loading data, message=FALSE, warning=FALSE, include=FALSE}
rm(list = ls())

# load packages 
for (pkg in c("tidyverse", "igraph", "visNetwork", "data.table", "R.utils", "RPostgreSQL", "cowplot", "maditr", "stringr", "stringi", "mosaic", "sf", "raster", "dplyr", "spData", "spDataLarge", "tmap", "leaflet", "mapview", "ggplot2", "shiny", "maps", "plotly", "RColorBrewer", "leaflet.extras", "rgdal", "stats")) {
  library(pkg, character.only = TRUE)
}


# connect to postgresql to get our data
conn <- dbConnect(drv = PostgreSQL(), 
                  dbname = "sdad", 
                  host = "10.250.124.195", 
                  port = 5432, 
                  user = Sys.getenv("db_userid"), 
                  password = Sys.getenv("db_pwd"))

# query the users_gh data from github data 
users_gh <- dbGetQuery(conn, "SELECT login, created_at, city, state, country_code, location, long, lat
                              FROM gh.ctrs_raw")

desc_ctrs_summary <- dbGetQuery(conn, "SELECT *
                              FROM gh.desc_ctrs_summary")

# disconnect from postgresql database 
dbDisconnect(conn)

source("~/git/dspg20oss/src/geographic/00_functions.R", echo = T, prompt.echo = "", spaced = F)
```

There are 2.24% (N=48079) github users (gh.users_gh) are missing commit/repo contributions (gh.desc_ctrs_summary). We excluded these 48079 users for our analysis.
```{r message=FALSE, warning=FALSE}
#desc_ctrs_summary <- desc_ctrs_summary%>%
#  mutate(check = "A")
users_gh_ctrs <- users_gh%>%
  mutate(missing_geo = if_else(is.na(country_code) | is.na(city), T, F))%>%
  left_join(desc_ctrs_summary, by = "login")
users_gh_ctrs <- as.data.table(users_gh_ctrs)

table(users_gh_ctrs$missing_geo)
nrow(users_gh_ctrs)
#table(is.na(users_gh_ctrs$check))

```

# Measurements for contributions
We use the number of commits, repos, additions and deletions as measurements for contributions to open source softwares. However, these numeric values are heavily skewed. We won't be able to conduct t-test for our hypothesis testing if the valuese are not approximately normally distributed.
```{r message=FALSE, warning=FALSE}
users_gh_ctrs_gather <- users_gh_ctrs%>%
  select(login, missing_geo, repos, commits, deletions, additions)%>%
  gather("ctrs", "counts", -c(login, missing_geo))

users_gh_ctrs_gather$missing_geo <- as.character(users_gh_ctrs_gather$missing_geo)
#glimpse(users_gh_ctrs_gather)

ggplot(users_gh_ctrs_gather, aes(x=ctrs, y=counts, color=missing_geo)) +
  geom_boxplot()
```

# Methods for skewed data
First, we exclude outliers (>= 172), and then we took the logged commits numbers. We say that the number of commits is approximately normally distributed. 
```{r message=FALSE, warning=FALSE}
exclude_outlier <- function(dt = users_gh_ctrs , var = "commits"){
  index <- grep(var, colnames(dt))
  q1 <- quantile(dt[,..index], probs=0.25, na.rm=T)	
  q3 <- quantile(dt[,..index],probs=0.75, na.rm=T)
  IQR <- q3-q1
  lb <- q1- 1.5 * IQR
  ub <- q3 + 1.5 * IQR
  
  dt <- dt%>%
    filter(dt[,..index] < ub)
  dt$var_t <- log(dt[,..index])
  return(dt)
}

```

# Hypothesis Test for the number of commits
$H_0$: The average number of commits among github users who have geo info is the same as the github users who do not have geo info.
$H_A$: The average number of commits among github users who have geo info is different from those who do not have geo info.

Given p-value is approximately 0, we reject $H_0$ and conclude that there the average number of commits among github users who have geo info is statistically significantly different from those who do not have geo info.
```{r message=FALSE, warning=FALSE}
users_gh_ctrs%>%
  group_by(missing_geo)%>%
  summarize(mean_commits = mean(commits, na.rm=T), sd_commits = sd(commits, na.rm=T))

users_gh_ctrs_commits <- exclude_outlier(dt = users_gh_ctrs , var = "commits")
ggplot(users_gh_ctrs_commits, aes(x = var_t))+
  geom_histogram(binwidth = 0.5)

boxplot(var_t~missing_geo,data=users_gh_ctrs_commits, main="Distribution of the number of commits between 2 groups",
   xlab="Missing geographic location", ylab="Number of commits")

t.test(users_gh_ctrs_commits$var_t~ users_gh_ctrs_commits$missing_geo)
```


# Hypothesis Test for the number of repos
Repos is not normally distributed, can't perform t-test
```{r}
users_gh_ctrs%>%
  group_by(missing_geo)%>%
  summarize(mean_repos = mean(repos, na.rm=T), sd_commits = sd(repos, na.rm=T))

users_gh_ctrs_repos <- exclude_outlier(dt = users_gh_ctrs , var = "repos")
ggplot(users_gh_ctrs_repos, aes(x = var_t))+
  geom_histogram(binwidth = 0.5)

boxplot(var_t~missing_geo,data=users_gh_ctrs_repos, main="Distribution of the number of repositories between 2 groups",
   xlab="Missing geographic location", ylab="Number of repos")
```

# Hypothesis Test for the number of additions
$H_0$: The average number of additions among github users who have geo info is the same as the github users who do not have geo info.
$H_A$: The average number of additions among github users who have geo info is different from those who do not have geo info.

Before log, the average number of additions among gh users who have geo info was 16214, and the average number of additions among gh users who don't have go info was 11231. We are 95% confident that the actual difference between two groups is between 4895 and 5072, which does not inclue 0. We reject $H_0$ and conclude that there the average number of additions among github users who have geo info is statistically significantly different from those who do not have geo info.
```{r}
users_gh_ctrs%>%
  group_by(missing_geo)%>%
  summarize(mean_additions = mean(additions, na.rm=T), sd_commits = sd(additions, na.rm=T))


users_gh_ctrs_additions <- exclude_outlier(dt = users_gh_ctrs , var = "additions")

ggplot(users_gh_ctrs_additions, aes(var_t))+
  geom_histogram(binwidth = 1)

users_gh_ctrs_additions <-users_gh_ctrs_additions%>%
  mutate(var_t_z = var_t - mean(users_gh_ctrs_additions$var_t,na.rm=T)/sd(users_gh_ctrs_additions$var_t,na.rm=T))

summary(users_gh_ctrs_additions$var_t)

boxplot(var_t~missing_geo,data=users_gh_ctrs_additions, main="Distribution of the number of additions between 2 groups",
   xlab="Missing geographic location", ylab="Number of additions")

t.test(users_gh_ctrs_additions$var_t~ users_gh_ctrs_additions$missing_geo)
```


# Hypothesis Test for the number of deletions
$H_0$: The average number of deletions among github users who have geo info is the same as the github users who do not have geo info.
$H_A$: The average number of deletions among github users who have geo info is different from those who do not have geo info.

Before log, the average number of deletions among gh users who have geo info was 1154, and the average number of deletions among gh users who don't have go info was 740. We are 95% confident that the actual difference between two groups is between 406 and 421, which does not inclue 0. We reject $H_0$ and conclude that there the average number of deletions among github users who have geo info is statistically significantly different from those who do not have geo info.
```{r}
users_gh_ctrs_deletions <- exclude_outlier(dt = users_gh_ctrs , var = "deletions")
users_gh_ctrs_deletions <- users_gh_ctrs_deletions%>%
  filter(var_t != "-Inf")

summary(users_gh_ctrs_deletions$deletions)

ggplot(users_gh_ctrs_deletions, aes(var_t))+
  geom_histogram(binwidth = 1)

# ggplot(users_gh_ctrs_deletions, aes(x=var_t, y=var_t, color=missing_geo)) + 
#   geom_boxplot()

t.test(users_gh_ctrs_deletions$var_t~ users_gh_ctrs_deletions$missing_geo)
```






```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
#categorize commits
table(users_gh_ctrs$commits)
users_gh_ctrs <- users_gh_ctrs%>%
  mutate(commits_cat = if_else(commits <= 4, "less than commits",
                               if_else(commits == 2, "2 commits", "more than 2 commits")))

table(users_gh_ctrs$commits_cat)

ObsTab <- table(users_gh_ctrs$commits, users_gh_ctrs$missing_geo)

p <- chisq.test(ObsTab)$p.value


unlist(summary(aov(x~as.factor(y))))

```


